# Appendix

We do not conduct formal analyses of stock trend information for the
`r number_to_word(length(minor_regions_short))`
Pacific Herring minor SARs: `r commify(minor_regions_full_parens)`.
However, we do provide time series of
landed commercial catch (Figure \@ref(fig:app-minor-catch)),
biological data including weight-at-age (Figure \@ref(fig:app-minor-weight-at-age)) and proportion-at-age (Figure \@ref(fig:app-minor-proportions-at-age)),
as well as the spawn index (Figure \@ref(fig:app-minor-survey-indices))
from `r minor_start_yr_plot` to `r minor_end_yr`.

```{r app-minor-catch, fig.asp=0.45, fig.cap = paste0("Time series of total landed catch in thousands of tonnes of Pacific Herring from ", minor_start_yr_plot, " to ", minor_end_yr, " in the minor stock assessment regions. Legend: 'Other' represents the reduction, the food and bait, as well as the special use fishery; 'RoeGN' represents the roe gillnet fshery; and 'RoeSN' represents the roe seine fishery.")}
plot_catch(minor_catch,
           xlim = c(minor_start_yr_plot, minor_end_yr),
           translate = french)
```

```{r app-minor-weight-at-age, fig.asp=0.375, fig.cap = paste0("Time series of weight-at-age in kilograms (kg) for age-", age_highlight, " (circles) and ", nRollWA, "-year running mean weight-at-age (lines) for Pacific Herring from ", minor_start_yr_plot, " to ", minor_end_yr, " in the minor stock assessment regions. Lines show ", nRollWA, "-year running means for age-", min(as.integer(names(minor_wa)), na.rm=TRUE), " to age-", age_plus, " herring (incrementing higher from the lowest line); the thick black line highlights age-", age_highlight, " herring. Missing weight-at-age values (i.e., years where there are no biological samples) are imputed using one of two methods: missing values at the beginning of the time series are imputed by extending the frst non-missing value backwards; other missing values are imputed as the mean of the previous ", nRollWA, " years. Biological summaries only include samples collected using seine nets (commercial and test) due to size-selectivity of other gear types such as gillnet. The age-",  age_plus, " class is a `plus group' which includes fish ages ", age_plus, " and older. Note that vertical axes are cropped at ", wa_ylim[1], " and ", wa_ylim[2], " kg.")}
plot_wa(minor_wa,
        circle_age = 3,
        xlim = c(minor_start_yr_plot, minor_end_yr),
        ylim = wa_ylim,
        n_roll = nRollWA,
        translate = french)
```

```{r app-minor-proportions-at-age, fig.asp=0.45, fig.cap = paste0("Time series of proportion-at-age for Pacific Herring from ", minor_start_yr_plot, " to ", minor_end_yr, " in the minor stock assessment regions. The black line is the mean age, and the shaded area is the approximate ", ci_level*100, "\\% distribution. Biological summaries only include samples collected using seine nets (commercial and test) due to size-selectivity of other gear types such as gillnet. The age-", age_plus, " class is a `plus group' which includes fish ages ", age_plus, " and older.")}
plot_pa(minor_pa,
        age_plus = age_plus,
        conf = ci_level,
        xlim = c(minor_start_yr_plot, minor_end_yr),
        ylim = c(1, age_plus),
        translate = french)

```

```{r app-minor-survey-indices, fig.asp=0.45, fig.cap = paste0("Time series of spawn index in thousands of tonnes for Pacific Herring from ", minor_start_yr_plot, " to ", minor_end_yr, " in the minor stock assessment regions. The spawn index has two distinct periods defned by the dominant survey method: surface surveys (1951 to 1987), and dive surveys (1988 to 2018). The dashed vertical line is the boundary between these two periods. The `spawn index' represents the raw survey data only, and is not scaled by the spawn survey scaling parameter, q.")}
plot_spawn_ind(minor_surv,
               xlim = c(minor_start_yr_plot, minor_end_yr),
               new_surv_yr = new_surv_yr,
               translate = french)
```
