\setlength{\parindent}{0in} 
\setlength{\leftskip}{0in} 
\setlength{\parskip}{4pt}

# Appendix

We do not conduct formal analyses of stock trend information for the
`r number_to_word(length(minor_regions_short))`
Pacific Herring minor SARs: `r commify(minor_regions_full_parens)`.
However, we provide the spawn index from `r assess_yr - 9` to `r assess_yr` (Table \@ref(tab:app-minor-survey-indices-tab)).
We also provide time series of
landed commercial catch (Figure \@ref(fig:app-minor-catch)),
biological data including weight-at-age (Figure \@ref(fig:app-minor-weight-at-age)) and proportion-at-age (Figure \@ref(fig:app-minor-proportions-at-age)),
as well as the spawn index (Figure \@ref(fig:app-minor-survey-indices-fig))
from `r minor_start_yr_plot` to `r minor_end_yr`.

(ref:app-minor-survey-indices-tab-cap) Spawn index in tonnes of Pacific Herring in the minor stock assessment regions (SARs) from `r assess_yr-9` to `r assess_yr`.
Legend: `r commify(minor_regions_full_parens)`.
Notes: the 'spawn index' is not scaled by the spawn survey scaling parameter $q$,
and, if present, 'NA' indicates that data are not available.

(ref:app-minor-survey-indices-tab-cap-french) Not yet translated.

```{r app-minor-survey-indices-tab}
spawn_index_table(minor_surv_short,
                  by_vec = minor_regions_short,
                  first_yr = assess_yr - 9,
                  cap = ifelse(french, "(ref:app-minor-survey-indices-tab-cap-french)",
                               "(ref:app-minor-survey-indices-tab-cap)"),
                  french,
                  longtable = FALSE)
```

(ref:minor-catch-cap) Time series of total landed catch in thousands of tonnes (t) of Pacific Herring from `r minor_start_yr_plot` to `r minor_end_yr` in the minor stock assessment regions.
Legend: 'Other' represents the reduction, the food and bait, as well as the special use fishery; 'RoeGN' represents the roe gillnet fishery; and 'RoeSN' represents the roe seine fishery.

(ref:minor-catch-cap-french) Not yet translated.

```{r app-minor-catch, fig.asp=0.45, fig.cap = ifelse(french, "(ref:minor-catch-cap-french)", "(ref:minor-catch-cap)")}
plot_catch(minor_catch,
           xlim = c(minor_start_yr_plot, minor_end_yr),
           translate = french)
```

(ref:minor-wa-cap) Time series of weight-at-age in kilograms (kg) for age-`r age_highlight` (circles) and `r nRollWA`-year running mean weight-at-age (lines) for Pacific Herring from `r minor_start_yr_plot` to `r minor_end_yr` in the minor stock assessment regions.
Lines show `r nRollWA`-year running means for age-`r min(as.integer(names(minor_wa)), na.rm=TRUE)` to age-`r age_plus` herring (incrementing higher from the lowest line);
the thick black line highlights age-`r age_highlight` herring.
Missing weight-at-age values (i.e., years where there are no biological samples) are imputed using one of two methods:
missing values at the beginning of the time series are imputed by extending the frst non-missing value backwards;
other missing values are imputed as the mean of the previous `r nRollWA` years.
Biological summaries only include samples collected using seine nets (commercial and test) due to size-selectivity of other gear types such as gillnet.
The age-`r age_plus` class is a 'plus group' which includes fish ages `r age_plus` and older.
Note: vertical axes are cropped at `r wa_ylim[1]` and `r wa_ylim[2]` kg.

<!-- Need to fix automation (i.e., age-3) in french captions, here and elsewhere -->

(ref:minor-wa-cap-french) Not yet translated.

```{r app-minor-weight-at-age, fig.asp=0.375, fig.cap = ifelse(french, "(ref:minor-wa-cap-french)", "(ref:minor-wa-cap)")}
plot_wa(minor_wa,
        circle_age = 3,
        xlim = c(minor_start_yr_plot, minor_end_yr),
        ylim = wa_ylim,
        n_roll = nRollWA,
        translate = french)
```

(ref:minor-pa-cap) Time series of proportion-at-age for Pacific Herring from `r minor_start_yr_plot` to `r minor_end_yr` in the minor stock assessment regions.
The black line is the mean age, and the shaded area is the approximate `r ci_level*100`% distribution.
Biological summaries only include samples collected using seine nets (commercial and test) due to size-selectivity of other gear types such as gillnet.
The age-`r age_plus` class is a 'plus group' which includes fish ages `r age_plus` and older.

(ref:minor-pa-cap-french) Not yet translated.

```{r app-minor-proportions-at-age, fig.asp=0.45, fig.cap = ifelse(french, "(ref:minor-pa-cap-french)", "(ref:minor-pa-cap)")}
plot_pa(minor_pa,
        age_plus = age_plus,
        conf = ci_level,
        xlim = c(minor_start_yr_plot, minor_end_yr),
        ylim = c(1, age_plus),
        translate = french)

```

(ref:minor-spawn-index-cap) Time series of spawn index in thousands of tonnes (t) for Pacific Herring from `r minor_start_yr_plot` to `r minor_end_yr` in the minor stock assessment regions.
The spawn index has two distinct periods defned by the dominant survey method:
surface surveys (`r minor_start_yr` to `r new_surv_yr-1`), and
dive surveys (`r new_surv_yr` to `r minor_end_yr`).
The dashed vertical line is the boundary between these two periods.
Note: the 'spawn index' is not scaled by the spawn survey scaling parameter $q$.

(ref:minor-spawn-index-cap-french) Not yet translated.

```{r app-minor-survey-indices-fig, fig.asp=0.45, fig.cap = ifelse(french, "(ref:minor-spawn-index-cap-french)", "(ref:minor-spawn-index-cap)")}
plot_spawn_ind(minor_surv,
               xlim = c(minor_start_yr_plot, minor_end_yr),
               new_surv_yr = new_surv_yr,
               translate = french)
```
