# Haida Gwaii diagnostics

This section contains Markov chain Monte Carlo (MCMC) diagnostics for the
Haida Gwaii major stock assessment region SCA model.
These diagnostics will not be included in the final Science Response.

(ref:hg-priors-posts-figure) Prior probability distributions (lines) with
comparative posterior histograms (bars) used in the Haida Gwaii major stock assessment region.
The dotted red lines are the maximum posterior density estimates.
See Table \@ref(tab:hg-parameter-est-table) for description.

```{r hg-priors-posts-figure, fig.cap = "(ref:hg-priors-posts-figure)"}
model_ind <- match(en2fr("HG", french), major_regions_short)
make.priors.posts.plot(major_models[[model_ind]],
                       priors.only = FALSE)
```

(ref:hg-traces-figure) Trace plots for Markov chain Monte Carlo (MCMC) output of
estimated parameters for the Haida Gwaii major stock assessment region.
The MCMC run had chain length `r mcmc_length`
with a sample taken every `r f(mcmc_samp_freq)`^th^ iteration.
See Table \@ref(tab:hg-parameter-est-table) for description.
In addition, $B_0$ is unfished biomass,
$\mli{SB}_0$ is unfished spawning biomass,
$\mli{SSB}$ is spawning biomass,
$\hat{a}_k$ is selectivity-at-age-50%, and
$\hat{\gamma}_k$ is selectivity standard deviation-at-50%.
Subscripts represent gears as follows:
$k=1$ is other fisheries, $k=2$ is roe seine, $k=3$ is roe gillnet.

```{r hg-traces-figure, fig.asp=1, fig.cap="(ref:hg-traces-figure)"}
make.traces.plot(major_models[[model_ind]],
                 axis.lab.freq = 200)
```

(ref:hg-autocor-figure) Auto-correlation plots for Markov chain Monte Carlo (MCMC) output of
estimated parameters for the Haida Gwaii major stock assessment region.
See Table \@ref(tab:hg-parameter-est-table) and
Figure \@ref(fig:hg-traces-figure) for description.

```{r hg-autocor-figure, fig.asp=1, fig.cap = "(ref:hg-autocor-figure)"}
make.autocor.plot(major_models[[model_ind]])
```

(ref:hg-pairs-figure) Pairs plots for Markov chain Monte Carlo (MCMC) output of
estimated parameters for the Haida Gwaii major stock assessment region.
See Table \@ref(tab:hg-parameter-est-table) and
Figure \@ref(fig:hg-traces-figure) for description.

```{r hg-pairs-figure, fig.asp=1, fig.cap = "(ref:hg-pairs-figure)"}
make.pairs.plot(major_models[[model_ind]])
```

(ref:hg-biomass-retro-figure) Maximum posterior density of spawning biomass
with retrospectives for the Haida Gwaii major stock assessment region.

```{r hg-biomass-retro-figure, fig.cap = "(ref:hg-biomass-retro-figure)"}
biomass.plot.mpd(major_models[[model_ind]],
                 xlim = c(1972, assess_yr))
```
