# Haida Gwaii diagnostics

This section contains Markov chain Monte Carlo (MCMC) diagnostics for the
statistical catch-age model in the Haida Gwaii major stock assessment region.
The MCMC run had chain length `r mcmc_length`
with a sample taken every `r f(mcmc_samp_freq)`^th^ iteration.
The first `r f(mcmc_burnin)` samples were discarded (burn-in), 
leaving `r f(mcmc_num_samples-mcmc_burnin)` samples for posteriors.
These diagnostics will not be included in the final document.

(ref:hg-priors-posts-cap) Prior probability distributions (lines) with
comparative posterior histograms (bars) used in the Haida Gwaii major stock assessment region.
Red dashed lines are maximum posterior density estimates.
Legend: ln is natural logarithm.
See Table \@ref(tab:hg-parameter-est) for description.

(ref:hg-priors-posts-cap-fr) Distributions de probabilité a priori (lignes)
et histogrammes a posteriori comparatifs (barres) utilisés dans la région d’évaluation des stocks majeur de Haida Gwaii.
Les lignes rouges en pointillés sont des estimations de la densité a posteriori maximale.
Légende: ln est le logarithme naturel.
Voir le tableau \@ref(tab:hg-parameter-est) pour la description.

```{r hg-priors-posts, fig.cap=ifelse(french,"(ref:hg-priors-posts-cap-fr)","(ref:hg-priors-posts-cap)")}
model_ind <- match(en2fr("HG", french), major_regions_short)
make.priors.posts.plot(major_models[[model_ind]],
                       priors.only = FALSE)
```

(ref:hg-traces-cap) Trace plots for Markov chain Monte Carlo output of
estimated parameters for the Haida Gwaii major stock assessment region.
See Table \@ref(tab:hg-parameter-est) for description.
In addition, $B_0$ is unfished biomass,
$\SB_0$ is unfished spawning biomass,
$\SB$ is spawning biomass,
$\hat{a}$ is selectivity-at-age-50%, and
$\hat{\gamma}$ is selectivity standard deviation-at-50%.
Subscripts on $\hat{a}$ and $\hat{\gamma}$ represent gears as follows:
1 represents the reduction, the food and bait, as well as the special use fishery,
2 represents the roe gillnet fishery, and
3 represents the roe seine fishery.

(ref:hg-traces-cap-fr) Tracés des résultats de simulation Monte Carlo par chaîne de Markov pour les paramètres estimés
dans la région d’évaluation des stocks majeur de Haida Gwaii.
Voir le tableau \@ref(tab:hg-parameter-est) pour la description.
De plus, $\SB_0$ est la biomasse non exploitée estimée,
$\SB_0$ est la biomasse reproductrice non exploitée estimée,
$\SB$ est la biomasse reproductrice,
$\hat{a}$ est sélectivité selon l’âge à 50%, et
$\hat{\gamma}$ est écart-type de la sélectivité selon l’âge à 50%.
Les souscriptions sur $\hat{a}$ et $\hat{\gamma}$ représentent des engins comme suit:
1 représente la réduction, ainsi que les pêches pratiquées à des fins de subsistance, pour le marché des appâts et pour des usages spéciaux, 
2 représente la pêche au hareng rogué au filet maillant, et
3 représente la pêche au hareng rogué à la senne.

```{r hg-traces, fig.asp=1, fig.cap=ifelse(french, "(ref:hg-traces-cap-fr)", "(ref:hg-traces-cap)")}
make.traces.plot(major_models[[model_ind]],
                 axis.lab.freq = 200)
```

(ref:hg-autocor-cap) Auto-correlation plots for Markov chain Monte Carlo output of
estimated parameters for the Haida Gwaii major stock assessment region.
See Table \@ref(tab:hg-parameter-est) and Figure \@ref(fig:hg-traces) for description.

(ref:hg-autocor-cap-fr) Diagrammes d’autocorrélation des résultats de simulation Monte Carlo par chaîne de Markov pour les
paramètres estimés dans la région d’évaluation des stocks majeur de Haida Gwaii.
Voir le tableau \@ref(tab:hg-parameter-est) et la figure \@ref(fig:hg-traces) pour la description.

```{r hg-autocor, fig.asp=1, fig.cap=ifelse(french, "(ref:hg-autocor-cap-fr)", "(ref:hg-autocor-cap)")}
make.autocor.plot(major_models[[model_ind]])
```

(ref:hg-pairs-cap) Pairs plots for Markov chain Monte Carlo output of
estimated parameters for the Haida Gwaii major stock assessment region.
See Table \@ref(tab:hg-parameter-est) and Figure \@ref(fig:hg-traces) for description.

(ref:hg-pairs-cap-fr) Diagrammes par paires des résultats de simulation Monte Carlo par chaîne de Markov pour
les paramètres estimés dans la region d’évaluation des stocks majeur de Haida Gwaii.
Voir le tableau \@ref(tab:hg-parameter-est) et la figure \@ref(fig:hg-traces) pour la description.

```{r hg-pairs, fig.asp=1, fig.cap=ifelse(french, "(ref:hg-pairs-cap-fr)", "(ref:hg-pairs-cap)")}
make.pairs.plot(major_models[[model_ind]])
```

(ref:hg-biomass-retro-cap) Maximum posterior density of spawning biomass
from `r recent_catch_yr` to `r assess_yr` (base model)
with retrospectives (-1 to -`r retrospective_yrs` years)
for the Haida Gwaii major stock assessment region.

(ref:hg-biomass-retro-cap-fr) Densité a posteriori maximale de la biomasse reproductrice
de `r recent_catch_yr` à `r assess_yr` (modèle de base)
avec des rétrospectives (-1 à -`r retrospective_yrs` années)
pour la région d'évaluation des stocks majeur de Haida Gwaii.

```{r hg-biomass-retro, fig.cap=ifelse(french, "(ref:hg-biomass-retro-cap-fr)", "(ref:hg-biomass-retro-cap)")}
biomass.plot.mpd(major_models[[model_ind]],
                 xlim = c(recent_catch_yr, assess_yr),
                 translate = french)
```
