# Haida Gwaii diagnostics

This section contains Markov chain Monte Carlo (MCMC) diagnostics for the Haida Gwaii major stock assessment region SCA model.
These diagnostics will not be included in the final Science Response.

(ref:hg-priors-posts-figure) Prior probability distributions (lines) with comparative posterior histograms (bars) used in the Haida Gwaii major stock assessment region.
The dotted red lines are the maximum posterior density estimates.
See Table \@ref(tab:hg-parameter-est-table) for description.

```{r hg-priors-posts-figure, fig.cap = "(ref:hg-priors-posts-figure)"}
model_ind <- match(en2fr("HG", french), major_regions_short)
make.priors.posts.plot(major_models[[model_ind]],
                       priors.only = FALSE)
```

(ref:hg-traces-figure) Trace plots for Markov chain Monte Carlo (MCMC) output of estimated parameters for the Haida Gwaii major stock assessment region.
The MCMC run had chain length `r mcmc_length` with a sample taken every `r f(mcmc_samp_freq)`^th^ iteration.
See Table \@ref(tab:hg-parameter-est-table) for description.
In addition, $B_0$ is unfished biomass,
$\mli{SB}_0$ is unfished spawning biomass, and
$\mli{SSB}$ is spawning biomass.
Parameters $\hat{a}_k$ (selectivity-at-age-50%), and
$\hat{\gamma}_k$ (selectivity standard deviation-at-50%) represent gears as subscripts:
$k=1$: other fisheries, $k=2$: roe seine, $k=3$: row gillnet.

```{r hg-traces-figure, fig.asp=1, fig.cap="(ref:hg-traces-figure)"}
make.traces.plot(major_models[[model_ind]],
                 axis.lab.freq = 200)
```

(ref:hg-autocor-figure) Auto-correlation plots for Markov chain Monte Carlo (MCMC) output of estimated parameters for the Haida Gwaii major stock assessment region.
See Table \@ref(tab:hg-parameter-est-table) and Figure \@ref(fig:hg-traces-figure) for description.

```{r hg-autocor-figure, fig.asp=1, fig.cap = "(ref:hg-autocor-figure)"}
make.autocor.plot(major_models[[model_ind]])
```

(ref:hg-pairs-figure) Pairs plots for Markov chain Monte Carlo (MCMC) output of estimated parameters for the Haida Gwaii major stock assessment region.
See Table \@ref(tab:hg-parameter-est-table) and Figure \@ref(fig:hg-traces-figure) for description.
```{r hg-pairs-figure, fig.asp=1, fig.cap = "(ref:hg-pairs-figure)"}
make.pairs.plot(major_models[[model_ind]])
```

(ref:hg-biomass-retro-figure) Maximum posterior density spawning biomass with retrospectives for the Haida Gwaii major stock assessment region.
```{r hg-biomass-retro-figure, fig.cap = "(ref:hg-biomass-retro-figure)"}
biomass.plot.mpd(major_models[[model_ind]],
                 xlim = c(1972, assess_yr))
```
