# Prince Rupert District diagnostics

This section contains Markov chain Monte Carlo (MCMC) diagnostics for the Pacific Herring statistical catch-age model
in the Prince Rupert District major stock assessment region.
The MCMC run had chain length `r mcmc_length`
with a sample taken every `r f(mcmc_samp_freq)`^th^ iteration.
The first `r f(mcmc_burnin)` samples were discarded (burn-in), 
leaving `r f(mcmc_num_samples-mcmc_burnin)` samples for posteriors.
This section will not be included in the final document.

(ref:prd-priors-posts-cap) Prior probability distributions (lines) with
comparative posterior histograms (bars) for the Pacific Herring statistical catch-age model in the Prince Rupert District major stock assessment region.
See Table \@ref(tab:hg-parameter-est) and Figure \@ref(fig:hg-priors-posts) for description.

(ref:prd-priors-posts-cap-fr) Distributions de probabilité a priori (lignes)
et histogrammes a posteriori comparatifs (barres) pour le hareng du Pacifique dans la région d’évaluation des stocks majeur du district de Prince Rupert.
Voir le tableau \@ref(tab:hg-parameter-est) et la figure \@ref(fig:hg-priors-posts) pour la description.

```{r prd-priors-posts, fig.cap=ifelse(french, "(ref:prd-priors-posts-cap-fr)", "(ref:prd-priors-posts-cap)")}
model_ind <- match(en2fr("PRD", french), major_regions_short)
make.priors.posts.plot(major_models[[model_ind]],
                       priors.only = FALSE)
```

(ref:prd-traces-cap) Trace plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model
in the Prince Rupert District major stock assessment region.
See Table \@ref(tab:hg-parameter-est) and Figure \@ref(fig:hg-traces) for description.

(ref:prd-traces-cap-fr) Tracés des résultats de simulation Monte Carlo par chaîne de Markov pour les paramètres estimés pour le hareng du Pacifique
dans la région d’évaluation des stocks majeur du district de Prince Rupert.
Voir le tableau \@ref(tab:hg-parameter-est) et la figure \@ref(fig:hg-traces) pour la description.

```{r prd-traces, fig.asp=1, fig.cap=ifelse(french, "(ref:prd-traces-cap-fr)", "(ref:prd-traces-cap)")}
make.traces.plot(major_models[[model_ind]],
                 axis.lab.freq = 200)
```

(ref:prd-autocor-cap) Auto-correlation plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model in the Prince Rupert District major stock assessment region.
See Table \@ref(tab:hg-parameter-est) and Figure \@ref(fig:hg-traces) for description.

(ref:prd-autocor-cap-fr) Diagrammes d’autocorrélation des résultats de simulation Monte Carlo par chaîne de Markov pour les paramètres estimés pour le hareng du Pacifique dans la région d’évaluation des stocks majeur du district de Prince Rupert.
Voir le tableau \@ref(tab:hg-parameter-est) et la figure \@ref(fig:hg-traces) pour la description.

```{r prd-autocor, fig.asp=1, fig.cap=ifelse(french, "(ref:prd-autocor-cap-fr)", "(ref:prd-autocor-cap)")}
make.autocor.plot(major_models[[model_ind]])
```

(ref:prd-pairs-cap) Pairs plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model in the Prince Rupert District major stock assessment region.
See Table \@ref(tab:hg-parameter-est) and Figure \@ref(fig:hg-traces) for description.

(ref:prd-pairs-cap-fr) Diagrammes par paires des résultats de simulation Monte Carlo par chaîne de Markov pour
les paramètres estimés pour le hareng du Pacifique dans la region d’évaluation des stocks majeur du district de Prince Rupert.
Voir le tableau \@ref(tab:hg-parameter-est) et la figure \@ref(fig:hg-traces) pour la description.

```{r prd-pairs, fig.asp=1, fig.cap=ifelse(french, "(ref:prd-pairs-cap-fr)", "(ref:prd-pairs-cap)")}
make.pairs.plot(major_models[[model_ind]])
```

(ref:prd-biomass-retro-cap) Maximum posterior density of spawning biomass (lines)
from `r recent_catch_yr` to `r assess_yr` (base model)
with retrospectives (-1 to -`r retrospective_yrs` years)
for the Pacific Herring statistical catch-age model in the Prince Rupert District major stock assessment region.
See Figure \@ref(fig:hg-biomass-retro) for description.

(ref:prd-biomass-retro-cap-fr) Densité a posteriori maximale de la biomasse reproductrice (lignes)
de `r recent_catch_yr` à `r assess_yr` (modèle de base)
avec des rétrospectives (-1 à -`r retrospective_yrs` années)
pour le hareng du Pacifique dans la région d'évaluation des stocks majeur du district de Prince Rupert.
Voir la figure \@ref(fig:hg-biomass-retro) pour la description.

```{r prd-biomass-retro, fig.cap=ifelse(french, "(ref:prd-biomass-retro-cap-fr)", "(ref:prd-biomass-retro-cap)")}
biomass.plot.mpd(major_models[[model_ind]],
                 xlim = c(recent_catch_yr, assess_yr),
                 translate = french)
```

(ref:prd-sr-cap) Relationship between spawning biomass in thousands of tonnes (t) and
the number of age-`r age_first` recruits in thousands of millions (points), as well as the
Beverton-Holt stock-recruitment relationship (line)
for the Pacific Herring statistical catch-age model in the Prince Rupert District major stock assessment region.
See Figure \@ref(fig:hg-sr) for description.

(ref:prd-sr-cap-fr) La relation entre la biomasse reproductrice en milliers de tonnes (t) et
le nombre de recrues d'âge `r age_first` en milliers de millions (points), ainsi que
la relation stock-recrutement du modèle Beverton-Holt (ligne)
pour le hareng du Pacifique dans la région d'évaluation des stocks majeur du district de Prince Rupert.
Voir la figure \@ref(fig:hg-sr) pour la description.

```{r prd-sr, fig.cap=ifelse(french, "(ref:prd-sr-cap-fr)", "(ref:prd-sr-cap)")}
plot_bh(major_models[[model_ind]],
        regions=major_regions_full[[model_ind]],
        translate=french)
```

(ref:hcr-prd-cap) `r paste0("Projected spawning biomass for ", assess_yr + 1, " compared to harvest rate and TAC for the Prince Rupert District, rows 1-4 in Table \\@ref(tab:decision-prd). Red horizontal and vertical lines show median harvest rate, TAC, and projected $\\SB_t$; mean statistics shown with green lines.")`
```{r hcr-prd, fig.cap="(ref:hcr-prd-cap)"}
region <- "PRD"
probs <- confidence_vals
cowplot::plot_grid(plot_hcr(mp.lst.prd[[1]][[1]],
                            sbt.prd,
                            mp = mp.prd[1,]$label,
                            region = region,
                            probs = probs),
                   plot_hcr(mp.lst.prd[[1]][[2]],
                            sbt.prd,
                            mp = mp.prd[2,]$label,
                            region = region,
                            probs = probs),
                   plot_hcr(mp.lst.prd[[1]][[3]],
                            sbt.prd,
                            mp = mp.prd[3,]$label,
                            region = region,
                            probs = probs,
                            show.x.axes = TRUE),
                   plot_hcr(mp.lst.prd[[1]][[4]],
                            sbt.prd,
                            mp = mp.prd[4,]$label,
                            region = region,
                            probs = probs,
                            show.x.axes = TRUE),
                   nrow = 2,
                   ncol = 2,
                   align = "hv",
                   axis = "tblr")
```

(ref:hcr-prd-2-cap) `r paste0("Projected spawning biomass for ", assess_yr + 1, " compared to harvest rate and TAC for the Prince Rupert District, rows 5-8 in Table \\@ref(tab:decision-prd). Red horizontal and vertical lines show median harvest rate, TAC, and projected $\\SB_t$; mean statistics shown with green lines.")`
```{r hcr-prd-2, fig.cap="(ref:hcr-prd-2-cap)"}
region <- "PRD"
probs <- confidence_vals 
cowplot::plot_grid(plot_hcr(mp.lst.prd[[1]][[5]],
                            sbt.prd,
                            mp = mp.prd[5,]$label,
                            region = region,
                            probs = probs),
                   plot_hcr(mp.lst.prd[[1]][[6]],
                            sbt.prd,
                            mp = mp.prd[6,]$label,
                            region = region,
                            probs = probs),
                   plot_hcr(mp.lst.prd[[1]][[7]],
                            sbt.prd,
                            mp = mp.prd[7,]$label,
                            region = region,
                            probs = probs,
                            show.x.axes = TRUE),
                   plot_hcr(mp.lst.prd[[1]][[8]],
                            sbt.prd,
                            mp = mp.prd[8,]$label,
                            region = region,
                            probs = probs,
                            show.x.axes = TRUE),
                   nrow = 2,
                   ncol = 2,
                   align = c("v", "h"))
```

(ref:hcr-prd-3-cap) `r paste0("Projected spawning biomass for ", assess_yr + 1, " compared to harvest rate and TAC for the Prince Rupert District, rows 9-10 in Table \\@ref(tab:decision-prd). Red horizontal and vertical lines show median harvest rate, TAC, and projected $\\SB_t$; mean statistics shown with green lines.")`
```{r hcr-prd-3, fig.cap="(ref:hcr-prd-3-cap)"}
region <- "PRD"
probs <- confidence_vals 
cowplot::plot_grid(plot_hcr(mp.lst.prd[[1]][[9]],
                            sbt.prd,
                            mp = mp.prd[9,]$label,
                            region = region,
                            probs = probs,
                            show.x.axes = TRUE),
                   plot_hcr(mp.lst.prd[[1]][[10]],
                            sbt.prd,
                            mp = mp.prd[10,]$label,
                            region = region,
                            probs = probs,
                            show.x.axes = TRUE),
                   nrow = 2,
                   ncol = 1,
                   align = c("v", "h"))
```
