# Prince Rupert District diagnostics

This section contains Markov chain Monte Carlo (MCMC) diagnostics for the
statistical catch-age model in the Prince Rupert District major stock assessment region.
The MCMC run had chain length `r mcmc_length`
with a sample taken every `r f(mcmc_samp_freq)`^th^ iteration.
The first `r f(mcmc_burnin)` samples were discarded (burn-in), 
leaving `r f(mcmc_num_samples-mcmc_burnin)` samples for posteriors.
These diagnostics will not be included in the final document.

(ref:prd-priors-posts-cap) Prior probability distributions (lines) with
comparative posterior histograms (bars) used in the Prince Rupert District major stock assessment region.
Red dashed lines are maximum posterior density estimates.
Legend: ln is natural logarithm.
See Table \@ref(tab:hg-parameter-est) for description.

(ref:prd-priors-posts-cap-fr) Distributions de probabilité a priori (lignes)
et histogrammes a posteriori comparatifs (barres) utilisés dans la région d’évaluation des stocks majeur du district de Prince Rupert.
Les lignes rouges en pointillés sont des estimations de la densité a posteriori maximale.
Légende: ln est le logarithme naturel.
Voir le tableau \@ref(tab:hg-parameter-est) pour la description.

```{r prd-priors-posts, fig.cap=ifelse(french, "(ref:prd-priors-posts-cap-fr)", "(ref:prd-priors-posts-cap)")}
model_ind <- match(en2fr("PRD", french), major_regions_short)
make.priors.posts.plot(major_models[[model_ind]],
                       priors.only = FALSE)
```

(ref:prd-traces-cap) Trace plots for Markov chain Monte Carlo output of
estimated parameters for the Prince Rupert District major stock assessment region.
See Table \@ref(tab:hg-parameter-est) and Figure \@ref(fig:hg-traces) for description.
In addition, $B_0$ is unfished biomass,
$\SB_0$ is unfished spawning biomass,
$\SB$ is spawning biomass,
$\hat{a}$ is selectivity-at-age-50%, and
$\hat{\gamma}$ is selectivity standard deviation-at-50%.
Subscripts on $\hat{a}$ and $\hat{\gamma}$ represent gears as follows:
1 is other fisheries, 2 is roe seine, and 3 is roe gillnet.

(ref:prd-traces-cap-fr) French caption.

```{r prd-traces, fig.asp=1, fig.cap=ifelse(french, "(ref:prd-traces-cap-fr)", "(ref:prd-traces-cap)")}
make.traces.plot(major_models[[model_ind]],
                 axis.lab.freq = 200)
```

(ref:prd-autocor-cap) Auto-correlation plots for Markov chain Monte Carlo output of
estimated parameters for the Prince Rupert District major stock assessment region.
See Table \@ref(tab:hg-parameter-est) and Figure \@ref(fig:prd-traces) for description.

(ref:prd-autocor-cap-fr) French caption.

```{r prd-autocor, fig.asp=1, fig.cap=ifelse(french, "(ref:prd-autocor-cap-fr)", "(ref:prd-autocor-cap)")}
make.autocor.plot(major_models[[model_ind]])
```

(ref:prd-pairs-cap) Pairs plots for Markov chain Monte Carlo output of
estimated parameters for the Prince Rupert District major stock assessment region.
See Table \@ref(tab:hg-parameter-est) and Figure \@ref(fig:prd-traces) for description.

(ref:prd-pairs-cap-fr) French caption.

```{r prd-pairs, fig.asp=1, fig.cap=ifelse(french, "(ref:prd-pairs-cap-fr)", "(ref:prd-pairs-cap)")}
make.pairs.plot(major_models[[model_ind]])
```

(ref:prd-biomass-retro-cap) Maximum posterior density of spawning biomass
with retrospectives for the Prince Rupert District major stock assessment region.

(ref:prd-biomass-retro-cap-fr) French caption.

```{r prd-biomass-retro, fig.cap=ifelse(french, "(ref:prd-biomass-retro-cap-fr)", "(ref:prd-biomass-retro-cap)")}
biomass.plot.mpd(major_models[[model_ind]],
                 xlim = c(1972, assess_yr))
```

(ref:hcr-prd-cap) `r paste0("Projected spawning biomass for ", assess_yr + 1, " compared to harvest rate and TAC for the Prince Rupert District, rows 1-4 in Table \\@ref(tab:decision-prd). Red horizontal and vertical lines show median harvest rate, TAC, and projected $\\SB_t$; mean statistics shown with green lines.")`
```{r hcr-prd, fig.cap="(ref:hcr-prd-cap)"}
region <- "PRD"
probs <- confidence_vals
cowplot::plot_grid(plot_hcr(mp.lst.prd[[1]][[1]],
                            sbt.prd,
                            mp = mp.prd[1,]$label,
                            region = region,
                            probs = probs),
                   plot_hcr(mp.lst.prd[[1]][[2]],
                            sbt.prd,
                            mp = mp.prd[2,]$label,
                            region = region,
                            probs = probs),
                   plot_hcr(mp.lst.prd[[1]][[3]],
                            sbt.prd,
                            mp = mp.prd[3,]$label,
                            region = region,
                            probs = probs,
                            show.x.axes = TRUE),
                   plot_hcr(mp.lst.prd[[1]][[4]],
                            sbt.prd,
                            mp = mp.prd[4,]$label,
                            region = region,
                            probs = probs,
                            show.x.axes = TRUE),
                   nrow = 2,
                   ncol = 2,
                   align = "hv",
                   axis = "tblr")
```

(ref:hcr-prd-2-cap) `r paste0("Projected spawning biomass for ", assess_yr + 1, " compared to harvest rate and TAC for the Prince Rupert District, rows 5-8 in Table \\@ref(tab:decision-prd). Red horizontal and vertical lines show median harvest rate, TAC, and projected $\\SB_t$; mean statistics shown with green lines.")`
```{r hcr-prd-2, fig.cap="(ref:hcr-prd-2-cap)"}
region <- "PRD"
probs <- confidence_vals 
cowplot::plot_grid(plot_hcr(mp.lst.prd[[1]][[5]],
                            sbt.prd,
                            mp = mp.prd[5,]$label,
                            region = region,
                            probs = probs),
                   plot_hcr(mp.lst.prd[[1]][[6]],
                            sbt.prd,
                            mp = mp.prd[6,]$label,
                            region = region,
                            probs = probs),
                   plot_hcr(mp.lst.prd[[1]][[7]],
                            sbt.prd,
                            mp = mp.prd[7,]$label,
                            region = region,
                            probs = probs,
                            show.x.axes = TRUE),
                   plot_hcr(mp.lst.prd[[1]][[8]],
                            sbt.prd,
                            mp = mp.prd[8,]$label,
                            region = region,
                            probs = probs,
                            show.x.axes = TRUE),
                   nrow = 2,
                   ncol = 2,
                   align = c("v", "h"))
```

(ref:hcr-prd-3-cap) `r paste0("Projected spawning biomass for ", assess_yr + 1, " compared to harvest rate and TAC for the Prince Rupert District, rows 9-10 in Table \\@ref(tab:decision-prd). Red horizontal and vertical lines show median harvest rate, TAC, and projected $\\SB_t$; mean statistics shown with green lines.")`
```{r hcr-prd-3, fig.cap="(ref:hcr-prd-3-cap)"}
region <- "PRD"
probs <- confidence_vals 
cowplot::plot_grid(plot_hcr(mp.lst.prd[[1]][[9]],
                            sbt.prd,
                            mp = mp.prd[9,]$label,
                            region = region,
                            probs = probs,
                            show.x.axes = TRUE),
                   plot_hcr(mp.lst.prd[[1]][[10]],
                            sbt.prd,
                            mp = mp.prd[10,]$label,
                            region = region,
                            probs = probs,
                            show.x.axes = TRUE),
                   nrow = 2,
                   ncol = 1,
                   align = c("v", "h"))
```
