# Strait of Georgia diagnostics

This section contains Markov chain Monte Carlo (MCMC) diagnostics for the
statistical catch-age model in the Strait of Georgia major stock assessment region.
The MCMC run had chain length `r mcmc_length`
with a sample taken every `r f(mcmc_samp_freq)`^th^ iteration.
The first `r f(mcmc_burnin)` samples were discarded (burn-in), 
leaving `r f(mcmc_num_samples-mcmc_burnin)` samples for posteriors.
These diagnostics will not be included in the final document.

(ref:sog-priors-posts-cap) Prior probability distributions (lines) with
comparative posterior histograms (bars) used in the Strait of Georgia major stock assessment region.
Red dashed lines are maximum posterior density estimates.
Legend: ln is natural logarithm.
See Table \@ref(tab:hg-parameter-est) for description.

(ref:sog-priors-posts-cap-fr) Distributions de probabilité a priori (lignes)
et histogrammes a posteriori comparatifs (barres) utilisés dans la région d’évaluation des stocks majeur du détroit de Georgie.
Les lignes rouges en pointillés sont des estimations de la densité a posteriori maximale.
Légende: ln est le logarithme naturel.
Voir le tableau \@ref(tab:hg-parameter-est) pour la description.

```{r sog-priors-posts, fig.cap=ifelse(french, "(ref:sog-priors-posts-cap-fr)", "(ref:sog-priors-posts-cap)")}
model_ind <- match(en2fr("SoG", french), major_regions_short)
make.priors.posts.plot(major_models[[model_ind]],
                       priors.only = FALSE)
```

(ref:sog-traces-cap) Trace plots for Markov chain Monte Carlo output of
estimated parameters for the Strait of Georgia major stock assessment region.
See Table \@ref(tab:hg-parameter-est) and Figure \@ref(fig:hg-traces) for description.

(ref:sog-traces-cap-fr) French caption.

```{r sog-traces, fig.asp=1, fig.cap=ifelse(french, "(ref:sog-traces-cap-fr)", "(ref:sog-traces-cap)")}
make.traces.plot(major_models[[model_ind]],
                 axis.lab.freq = 200)
```

(ref:sog-autocor-cap) Auto-correlation plots for Markov chain Monte Carlo output of
estimated parameters for the Strait of Georgia major stock assessment region.
See Table \@ref(tab:hg-parameter-est) and Figure \@ref(fig:hg-traces) for description.

(ref:sog-autocor-cap-fr) French caption.

```{r sog-autocor, fig.asp=1, fig.cap=ifelse(french, "(ref:sog-autocor-cap-fr)", "(ref:sog-autocor-cap)")}
make.autocor.plot(major_models[[model_ind]])
```

(ref:sog-pairs-cap) Pairs plots for Markov chain Monte Carlo output of
estimated parameters for the Strait of Georgia major stock assessment region.
See Table \@ref(tab:hg-parameter-est) and Figure \@ref(fig:hg-traces) for description.

(ref:sog-pairs-cap-fr) French caption.

```{r sog-pairs, fig.asp=1, fig.cap=ifelse(french, "(ref:sog-pairs-cap-fr)", "(ref:sog-pairs-cap)")}
make.pairs.plot(major_models[[model_ind]])
```

(ref:sog-biomass-retro-cap) Maximum posterior density spawning biomass
with retrospectives for the Strait of Georgia major stock assessment region.

(ref:sog-biomass-retro-cap-fr) French caption.

```{r sog-biomass-retro, fig.cap=ifelse(french, "(ref:sog-biomass-retro-cap-fr)", "(ref:sog-biomass-retro-cap)")}
biomass.plot.mpd(major_models[[model_ind]],
                 xlim = c(1972, assess_yr))
```

(ref:hcr-sog-cap) `r paste0("Projected spawning biomass for ", assess_yr + 1, " compared to harvest rate and TAC for the Strait of Georgia region, rows 1-4 in Table \\@ref(tab:decision-sog). Red horizontal and vertical lines show median harvest rate, TAC, and projected $\\SB_t$; mean statistics shown with green lines.")`
```{r hcr-sog, fig.cap="(ref:hcr-sog-cap)"}
region <- "SoG"
probs <- confidence_vals 
cowplot::plot_grid(plot_hcr(mp.lst.sog[[1]][[1]],
                            sbt.sog,
                            mp = mp.sog[1,]$label,
                            region = region,
                            probs = probs),
                   plot_hcr(mp.lst.sog[[1]][[2]],
                            sbt.sog,
                            mp = mp.sog[2,]$label,
                            region = region,
                            probs = probs),
                   plot_hcr(mp.lst.sog[[1]][[3]],
                            sbt.sog,
                            mp = mp.sog[3,]$label,
                            region = region,
                            probs = probs,
                            show.x.axes = TRUE),
                   plot_hcr(mp.lst.sog[[1]][[4]],
                            sbt.sog,
                            mp = mp.sog[4,]$label,
                            region = region,
                            probs = probs,
                            show.x.axes = TRUE),
                   nrow = 2,
                   ncol = 2,
                   align = "hv",
                   axis = "tblr")
```

(ref:hcr-sog-2-cap) `r paste0("Projected spawning biomass for ", assess_yr + 1, " compared to harvest rate and TAC for the Strait of Georgia region, rows 5-8 in Table \\@ref(tab:decision-sog). Red horizontal and vertical lines show median harvest rate, TAC, and projected $\\SB_t$; mean statistics shown with green lines.")`
```{r hcr-sog-2, fig.height=9, fig.cap="(ref:hcr-sog-2-cap)"}
region <- "SoG"
probs <- confidence_vals 
cowplot::plot_grid(plot_hcr(mp.lst.sog[[1]][[5]],
                            sbt.sog,
                            mp = mp.sog[5,]$label,
                            region = region,
                            probs = probs),
                   plot_hcr(mp.lst.sog[[1]][[6]],
                            sbt.sog,
                            mp = mp.sog[6,]$label,
                            region = region,
                            probs = probs),
                   plot_hcr(mp.lst.sog[[1]][[7]],
                            sbt.sog,
                            mp = mp.sog[7,]$label,
                            region = region,
                            probs = probs,
                            show.x.axes = TRUE),
                   plot_hcr(mp.lst.sog[[1]][[8]],
                            sbt.sog,
                            mp = mp.sog[8,]$label,
                            region = region,
                            probs = probs,
                            show.x.axes = TRUE),
                   nrow = 2,
                   ncol = 2,
                   align = c("v", "h"))
```

(ref:hcr-sog-3-cap) `r paste0("Projected spawning biomass for ", assess_yr + 1, " compared to harvest rate and TAC for the Strait of Georgia region, row 9 in Table \\@ref(tab:decision-sog). Red horizontal and vertical lines show median harvest rate, TAC, and projected $\\SB_t$; mean statistics shown with green lines.")`
```{r hcr-sog-3, fig.height=9, fig.cap="(ref:hcr-sog-3-cap)"}
region <- "SoG"
probs <- confidence_vals 
cowplot::plot_grid(plot_hcr(mp.lst.sog[[1]][[9]],
                            sbt.sog,
                            mp = mp.sog[9,]$label,
                            region = region,
                            probs = probs,
                            show.x.axes = TRUE),
                   nrow = 1,
                   ncol = 1,
                   align = c("v", "h"))
```
