# West Coast of Vancouver Island diagnostics

This section contains Markov chain Monte Carlo (MCMC) diagnostics for the
statistical catch-age model in the West Coast of Vancouver Island major stock assessment region.
The MCMC run had chain length `r mcmc_length`
with a sample taken every `r f(mcmc_samp_freq)`^th^ iteration.
The first `r f(mcmc_burnin)` samples were discarded (burn-in), 
leaving `r f(mcmc_num_samples-mcmc_burnin)` samples for posteriors.
These diagnostics will not be included in the final document.

(ref:wcvi-priors-posts-cap) Prior probability distributions (lines) with
comparative posterior histograms (bars) used in the West Coast of Vancouver Island major stock assessment region.
Red dashed lines are maximum posterior density estimates.
Legend: ln is natural logarithm.
See Table \@ref(tab:hg-parameter-est-table) for description.

(ref:wcvi-priors-posts-cap-fr) Distributions de probabilité a priori (lignes)
et histogrammes a posteriori comparatifs (barres) utilisés dans la région d’évaluation des stocks majeur de la côte ouest de l’île de Vancouver.
Les lignes rouges en pointillés sont des estimations de la densité a posteriori maximale.
Légende: ln est le logarithme naturel.
Voir le tableau \@ref(tab:hg-parameter-est-table) pour la description.

```{r wcvi-priors-posts, fig.cap=ifelse(french, "(ref:wcvi-priors-posts-cap-fr)", "(ref:wcvi-priors-posts-cap)")}
model_ind <- match(en2fr("WCVI", french), major_regions_short)
make.priors.posts.plot(major_models[[model_ind]],
                       priors.only = FALSE)
```

(ref:wcvi-traces-cap) Trace plots for Markov chain Monte Carlo output of
estimated parameters for the West Coast of Vancouver Island major stock assessment region.
See Table \@ref(tab:hg-parameter-est-table) for description.
In addition, $B_0$ is unfished biomass,
$\SB_0$ is unfished spawning biomass,
$\SB$ is spawning biomass,
$\hat{a}$ is selectivity-at-age-50%, and
$\hat{\gamma}$ is selectivity standard deviation-at-50%.
Subscripts on $\hat{a}$ and $\hat{\gamma}$ represent gears as follows:
1 is other fisheries, 2 is roe seine, and 3 is roe gillnet.

(ref:wcvi-traces-cap-fr) French caption.

```{r wcvi-traces, fig.asp=1, fig.cap=ifelse(french, "(ref:wcvi-traces-cap-fr)", "(ref:wcvi-traces-cap)")}
make.traces.plot(major_models[[model_ind]],
                 axis.lab.freq = 200)
```

(ref:wcvi-autocor-cap) Auto-correlation plots for Markov chain Monte Carlo output of
estimated parameters for the West Coast of Vancouver Island major stock assessment region.
See Table \@ref(tab:hg-parameter-est-table) and
Figure \@ref(fig:wcvi-traces) for description.

(ref:wcvi-autocor-cap-fr) French caption.

```{r wcvi-autocor, fig.asp=1, fig.cap=ifelse(french, "(ref:wcvi-autocor-cap-fr)", "(ref:wcvi-autocor-cap)")}
make.autocor.plot(major_models[[model_ind]])
```

(ref:wcvi-pairs-cap) Pairs plots for Markov chain Monte Carlo output of
estimated parameters for the West Coast of Vancouver Island major stock assessment region.
See Table \@ref(tab:hg-parameter-est-table) and
Figure \@ref(fig:wcvi-traces) for description.

(ref:wcvi-pairs-cap-fr) French caption.

```{r wcvi-pairs, fig.asp=1, fig.cap=ifelse(french, "(ref:wcvi-pairs-cap-fr)", "(ref:wcvi-pairs-cap)")}
make.pairs.plot(major_models[[model_ind]])
```

(ref:wcvi-biomass-retro-cap) Maximum posterior density spawning biomass
with retrospectives for the West Coast of Vancouver Island major stock assessment region.

(ref:wcvi-biomass-retro-cap-fr) French caption.

```{r wcvi-biomass-retro, fig.cap=ifelse(french, "(ref:wcvi-biomass-retro-cap-fr)", "(ref:wcvi-biomass-retro-cap)")}
biomass.plot.mpd(major_models[[model_ind]],
                 xlim = c(1972, assess_yr))
```
