# West Coast of Vancouver Island diagnostics

This section contains MCMC diagnostics for the West Coast of Vancouver Island major stock assessment region SCA model.
These tables and figures will not be included in the final Science Response.

```{r wcvi-parameter-est-table, results = 'asis', echo = FALSE}
cap <- paste0("Posterior (5\\textsuperscript{th}, 50\\textsuperscript{th}, ",
              "and 95\\textsuperscript{th} percentile) and maximum posterior ",
              "density (MPD) estimates of key ",
              "parameters for the West Coast of Vancouver Island major stock ",
              "assessment region. Subscripts on $q$ ",
              "(catchability) indicate: 1 = surface survey, 2 = dive survey. ",
              "Tau ($\\tau$) and sigma ($\\sigma$) are calculated values.")
model_ind <- match(en2fr("WCVI", french), major_regions_short)
make.parameters.est.table(major_models[[model_ind]],
                          xcaption = cap,
                          xlabel = "tab:wcvi-parameter-est-table",
                          font.size = 11,
                          space.size = 12,
                          placement = "H")
```

```{r wcvi-recruitment-table, results = 'asis', echo = FALSE}
cap <- paste0("Posterior (5\\textsuperscript{th}, 50\\textsuperscript{th}, ",
              "and 95\\textsuperscript{th} percentile) and maximum posterior ",
              "density (MPD) estimates of ",
              "recruitment (millions) for the West Coast of Vancouver Island ",
              "major stock assessment region.")
make.value.table(major_models[[model_ind]],
                 type = 2,
                 syr = 2007,
                 xcaption = cap,
                 xlabel = "tab:wcvi-recruitment-table",
                 font.size = 11,
                 space.size = 12,
                 placement = "H")
                 ##tabular.environment = "longtable")
```

```{r wcvi-priors-posts-figure, fig.cap = "Prior probability distributions (lines) with comparative posterior histograms (bars) used in the West Coast of Vancouver Island major stock assessment region. Subscripts on $q$ (catchability) indicate: 1 = surface survey, 2 = dive survey. The dotted red lines are the maximum posterior density estimates."}
make.priors.posts.plot(major_models[[model_ind]],
                       priors.only = FALSE)
```

```{r wcvi-traces-figure, fig.asp=1, fig.cap = paste0("Trace plots for MCMC output of estimated parameters for the West Coast of Vancouver Island major stock assessment region. The MCMC run had chain length ", mcmc_length, " with a sample taken at every ", f(mcmc_samp_freq), "th iteration. Subscripts on $q$ (catchability) indicate: 1 = surface survey, 2 = dive survey. Parameters $\\hat{a}_k$ (selectivity-at-age-50\\%), and $\\hat{\\gamma}_k$ (selectivity standard deviation-at-50\\%) represent gears as follows: $k=1$: Other fisheries, $k=2$: Roe seine, $k=3$: Gillnet roe.")}
make.traces.plot(major_models[[model_ind]],
                 axis.lab.freq = 200)
```

(ref:wcvi-autocor-figure) Autocorrelation plots for MCMC output of estimated parameters for the West Coast of Vancouver Island major stock assessment region. See Figure \@ref(fig:wcvi-traces-figure) for parameter descriptions.
```{r wcvi-autocor-figure, fig.asp=1, fig.cap = "(ref:wcvi-autocor-figure)"}
make.autocor.plot(major_models[[model_ind]])
```

(ref:wcvi-pairs-figure) Pairs plots for MCMC output of estimated parameters for the West Coast of Vancouver Island major stock assessment region. See Figure \@ref(fig:wcvi-traces-figure) for parameter descriptions.
```{r wcvi-pairs-figure, fig.asp=1, fig.cap = "(ref:wcvi-pairs-figure)"}
make.pairs.plot(major_models[[model_ind]])
```

(ref:wcvi-biomass-retro-figure) Maximum posterior density biomass with retrospectivces for the West Coast of Vancouver Island major stock assessment region.
```{r wcvi-biomass-retro-figure, fig.cap = "(ref:wcvi-biomass-retro-figure)"}
biomass.plot.mpd(major_models[[model_ind]])
```


