# MCMC Diagnostics for the West Coast Vancouver Island iSCAM model

These tables and figures will not be included in the final Science Response.

```{r wcvi-parameter-est-table, results = 'asis', echo = FALSE}
cap <- paste0("Posterior (5\\textsuperscript{th} percentile, Median, and ",
              "95\\textsuperscript{th} percentile) and MPD estimates of key ",
              "parameters from the West Coast Vancouver Island AM2 model. Subscripts on $q$ ",
              "(catchability) indicate: 1 = Surface survey, 2 = Dive survey. ",
              "Tau ($\\tau$) and sigma ($\\sigma$) are calculated values.")
model_ind <- match(en2fr("WCVI", french), major_regions_short)
make.parameters.est.table(major_models[[model_ind]],
                          xcaption = cap,
                          xlabel = "tab:wcvi-parameter-est-table",
                          font.size = 11,
                          space.size = 12,
                          placement = "H")
```

```{r wcvi-spawning-biomass-depletion-table, results = 'asis', echo = FALSE}
cap <- paste0("Posterior (5\\textsuperscript{th} percentile, Median, and ",
              "95\\textsuperscript{th} percentile) and MPD estimates of ",
              "spawning biomass (1000 t) and relative spawning ",
              "biomass for the West Coast Vancouver Island AM2 model.")
make.biomass.depletion.table(major_models[[model_ind]],
                             syr = 2007,
                             xcaption = cap,
                             xlabel = "wcvi-spawning-biomass-depletion-table",
                             font.size = 11,
                             space.size = 12,
                             placement = "H")
                             ##tabular.environment = "longtable")
```

```{r wcvi-recruitment-table, results = 'asis', echo = FALSE}
cap <- paste0("Posterior (5\\textsuperscript{th} percentile, Median, and ",
              "95\\textsuperscript{th} percentile) and MPD estimates of ",
              "recruitment (millions) for the West Coast Vancouver Island AM2 model.")
make.value.table(major_models[[model_ind]],
                 type = 2,
                 syr = 2007,
                 xcaption = cap,
                 xlabel = "tab:wcvi-recruitment-table",
                 font.size = 11,
                 space.size = 12,
                 placement = "H")
                 ##tabular.environment = "longtable")
```

```{r wcvi-priors-posts-figure, fig.cap = "Prior probability distributions (lines) with comparative posterior histograms (bars) used in the West Coast Vancouver Island AM2 model. Parameters $q_k$ represent gears where: $k=1$ is the surface survey and $k=2$ is the dive survey. The dotted red lines are the MPD estimates."}
make.priors.posts.plot(major_models[[model_ind]],
                       priors.only = FALSE)
```

```{r wcvi-traces-figure, fig.cap = paste0("Trace plots for MCMC output of estimated parameters for the West Coast Vancouver Island AM2 model. The MCMC run had chain length ", mcmc_length, " with a sample taken at every ", f(mcmc_samp_freq), "th iteration. The catchability parameter $q_1$ represents the surface survey and $q_2$ the dive survey. Parameters $\\hat{a}_k$ (selectivity-at-age-50\\%), and $\\hat{\\gamma}_k$ (selectivity standard deviation-at-50\\%) represent gears as follows: $k=1$: Other fisheries, $k=2$: Roe seine, $k=3$: Gillnet roe.")}
make.traces.plot(major_models[[model_ind]],
                 axis.lab.freq = 200)
```

(ref:wcvi-autocor-figure) Autocorrelation plots for MCMC output of estimated parameters for the West Coast Vancouver Island AM2 model. See Figure \@ref(fig:wcvi-traces-figure) for parameter descriptions.
```{r wcvi-autocor-figure, fig.cap = "(ref:wcvi-autocor-figure)"}
make.autocor.plot(major_models[[model_ind]])
```

(ref:wcvi-pairs-figure) Pairs plots for MCMC output of estimated parameters in for the West Coast Vancouver Island AM2 model. See Figure \@ref(fig:wcvi-traces-figure) for parameter descriptions.
```{r wcvi-pairs-figure, fig.cap = "(ref:wcvi-pairs-figure)"}
make.pairs.plot(major_models[[model_ind]])
```

(ref:wcvi-biomass-retro-figure) MPD biomass with retrospectivces for the West Coast Vancouver Island AM2 model.
```{r wcvi-biomass-retro-figure, fig.cap = "(ref:wcvi-biomass-retro-figure)"}
biomass.plot.mpd(major_models[[model_ind]])
```


