---
t_title: "Stock status update with application of management procedures for Pacific Herring (*Clupea pallasii*) in British Columbia`:` Status in 2023 and forecast for 2024"
t_title_other: "Mise à jour de l'état des stocks avec application des procédures de gestion pour le hareng du Pacifique (*Clupea pallasii*) en Colombie-Britannique`:` État en 2023 et prévisions pour 2024"
assess_year: 2023
work_done_year: 2023
t_work_done_month: Month
report_number: 000
isbn_en: 978-0-660-00000-1
isbn_fr: 978-0-660-00000-2
t_approver: "Andrew Thomson \n\n\n Regional Director"
approval_year: 2023
t_approval_month: September
approval_day: 22
process_year: 2023
t_process_month: September
process_day: 22
t_branch: Science Branch
t_region: Pacific Region
output:
  csasdown:::sr_pdf:
    french: FALSE
    prepub: FALSE
    copy_sty: TRUE
    line_nums: FALSE
    line_nums_mod: 1
    draft_watermark: FALSE
    highlight: tango
type: sr
knit: bookdown::render_book
site: bookdown::bookdown_site
link-citations: TRUE
bibliography: bib/refs.bib
# bibliography: bib/refs_fr.bib
lot: TRUE
lof: TRUE
header-includes:
  - \usepackage{needspace}
  - \usepackage{afterpage}
---

\sloppy

```{r libraries, echo=FALSE, cache=FALSE, message=FALSE, results='hide', warning=FALSE}
library(knitr)
library(rmarkdown)
library(stringr)
library(tidyverse)
library(directlabels)
library(reshape2)
library(kableExtra)
library(here)
library(rosettafish)
library(csasdown)
library(gfutilities)
library(gfiscamutils)
library(ggrepel)
library(herringutils)
library(gcookbook)
library(readr)
library(zoo)
```

```{r setup, echo=FALSE, cache=FALSE, message=FALSE, results='hide', warning=FALSE}
if (is_latex_output()) {
  knitr_figs_dir <- "knitr-figs-pdf/"
  knitr_cache_dir <- "knitr-cache-pdf/"
  fig_out_type <- "pdf"
} else {
  knitr_figs_dir <- "knitr-figs-docx/"
  knitr_cache_dir <- "knitr-cache-docx/"
  fig_out_type <- "ragg_png"
}

fig_asp <- 0.618
fig_width <- 6.5
fig_out_width <- "6.5in"
fig_dpi <- 320
fig_align <- "center"
fig_pos <- "ht"
opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.path = knitr_figs_dir,
  cache.path = knitr_cache_dir,
  fig.asp = fig_asp,
  fig.width = fig_width,
  out.width = fig_out_width,
  echo = FALSE,
  cache.comments = FALSE,
  dev = fig_out_type,
  dpi = fig_dpi,
  fig.align = fig_align,
  fig.pos = "H"
)

options(
  xtable.comment = FALSE,
  kableExtra.latex.load_packages = FALSE,
  width = 80,
  scipen = 999,
  dplyr.summarise.inform = FALSE,
  ggrepel.max.overlaps = Inf
)
```

```{r metadata}
assess_yr <- metadata$assess_year
meta_out <- metadata$output

if (is.null(meta_out)) {
  options(french = FALSE)
} else {
  if (length(grep("pdf", names(meta_out)))) {
    french <- meta_out$`csasdown:::sr_pdf`$french
    options(french = french)
    prepub <- meta_out$`csasdown:::sr_pdf`$prepub
  } else if (length(grep("word", names(meta_out)))) {
    french <- meta_out$`csasdown::sr_word`$french
    options(french = french)
    prepub <- meta_out$`csasdown::sr_word`$prepub
  }
}

if (french) {
  t_title <- metadata$t_title_other
  t_title_other <- metadata$t_title
  t_title_short <- paste("État du hareng du Pacifique en", assess_yr,
                         "et prévisions pour", assess_yr + 1)
  t_isbn <- metadata$isbn_fr
  t_csl <- "csl/csas-french.csl"
  options(OutDec = ",")
} else {
  t_title <- metadata$t_title
  t_title_other <- metadata$t_title_other
  t_title_short <- paste("Pacific Herring status in", assess_yr,
                         "and forecast for", assess_yr + 1)
  t_isbn <- metadata$isbn_en
  t_csl <- "csl/csas.csl"
}

t_work_done_month <- en2fr(
  metadata$t_work_done_month, translate = french, case = "title"
)
t_approver <- gsub(
  pattern = "Regional Director",
  x = metadata$t_approver,
  replacement = en2fr(x = "Regional Director",
                      translate = french, case = "title")
)
t_approval_month <- en2fr(
  metadata$t_approval_month, translate = french, case = "title"
)
t_process_month <- en2fr(
  metadata$t_process_month, translate = french, case = "title"
)
t_branch <- en2fr(metadata$t_branch, translate = french, case = "title")
t_region <- en2fr(metadata$t_region, translate = french, case = "title")

t_cat_no <- paste0(
  "Fs70-7/",
  metadata$work_done_year,
  "-",
  str_pad(string = metadata$report_number, width = 3, pad = "0"),
  ifelse(french, "F", "E"),
  "PDF"
)
```

```{r models, cache=FALSE}
models_dir <- here("models")
major_stock_dir <- list("HG", "PRD", "CC", "SoG", "WCVI")
minor_stock_dir <- list("A27", "A2W")
special_stock_dir <- list("A10")

mcmc_length <- 20000000 # Default: 20,000,000
mcmc_samp_freq <- 4000  # Default: 4,000
mcmc_burnin <- 1000     # Default: 1,000
retro_yrs <- 1:10       # Default: 1:10

run_sca_models <- FALSE            # Run SCA for SARs in `major_stock_dir`
rebuild_rdata_model_files <- FALSE # Rebuild RData files (replace existing)
run_retros <- FALSE                # Run retrospectives

source(here("R", "run-sca.R"))
source(here("R", "model-setup.R"))
source(here("R", "variable-setup.R"))
source(here("R", "hcr.R"))

theme_set(herring_theme())
```

```{r output-options}
keep_non_CC <- TRUE     # FALSE to provide preliminary CC report
show_ic_figures <- TRUE # Show/hide incidental catch figures
slides <- FALSE         # Make figures for powerpoint slides
```

<!-- Distributions -->
\newcommand{\dUnif}[2]{$\mathcal{U}\left(#1, #2\right)$}
\newcommand{\dNorm}[2]{$\mathcal{N}\left(#1, #2\right)$}
\newcommand{\dLognorm}[2]{$\emph{Lognormal}\left(#1, #2\right)$}
\newcommand{\dBeta}[2]{$\emph{Beta}\left(#1, #2\right)$}
\newcommand{\dGamma}[2]{$\emph{Gamma}\left(#1, #2\right)$}

<!-- Other math -->
\newcommand{\lognorm}{\text{ln}}
\newcommand{\SB}{\mli{`r en2fr("SB", translate = french)`}}
\newcommand{\BR}{\mli{BR}}
\newcommand{\AVE}{\text{`r en2fr("AVE", translate = french)`}}

---
title: `r t_title`
title_other: `r t_title_other`
title_short: `r t_title_short`
isbn: `r t_isbn`
approver: `r t_approver`
approval_month: `r t_approval_month`
work_done_month: `r t_work_done_month`
branch: `r t_branch`
region: `r t_region`
cat_no: `r t_cat_no`
process_month: `r t_process_month`
csl: `r t_csl`
---

<!-- Compile the PDF on the command line: -->
<!-- bookdown::render_book("index.Rmd") -->
