\clearpage

# Haida Gwaii diagnostics

This section contains Markov chain Monte Carlo (MCMC) diagnostics
for the Pacific Herring statistical catch-age model
in the Haida Gwaii major stock assessment region.
The MCMC run had chain length `r number_to_word(mcmc_length)`
with a sample taken every `r number_to_word(mcmc_samp_freq)` iterations
(i.e., thinning).
The first `r number_to_word(mcmc_burnin)` samples were discarded (i.e., burn-in),
leaving `r number_to_word(mcmc_num_samples)` samples for posteriors.
This section will not be included in the final document.

Autocorrelation was detected within a number of the parameters. Inline with procedures used on WCVI parameter priors were reparameterized. For logarithmic natural mortality the normal prior was set to and initial value of -.5, the upper bound was reduced from 5 to 2, and the mean was shifted from -0.8 to -0.5. For logarithmic initial recruitment the uniform prior was changed to a normal distribution with mean 5 and a still wide sd of 15. The sd for selectivity for gears 2 and 3 was widened from 0.25 to 0.5. For the logarithmic catchability quotient for surface surveys the uniform prior was changed to a normal distribution with mean 0.0 and sd 0.2. 

(ref:hg-priors-posts-cap) Haida Gwaii SAR:
prior probability distributions (lines) with
comparative posterior histograms (bars)
for the Pacific Herring statistical catch-age model.
Red dashed lines are maximum posterior density estimates.
Legend: ln is natural logarithm.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables} for description.

(ref:hg-priors-posts-cap-fr) Distributions de probabilité a priori (lignes)
et histogrammes a posteriori comparatifs (barres)
pour le hareng du Pacifique dans la région d’évaluation des stocks
majeur de Haida Gwaii.
Les lignes rouges en pointillés sont des estimations
de la densité a posteriori maximale.
Légende: ln est le logarithme naturel.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}
pour la description.

```{r hg-priors-posts, fig.cap=ifelse(french,"(ref:hg-priors-posts-cap-fr)","(ref:hg-priors-posts-cap)")}
model_ind <- match(en2fr("HG", french), major_regions_short)
make.priors.posts.plot(
  model = major_models[[model_ind]],
  priors.only = FALSE
)
```

(ref:hg-traces-cap) Haida Gwaii SAR:
trace plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables} for description.
In addition, $B_0$ is unfished biomass,
$\SB_0$ is unfished spawning biomass,
$\SB$ is spawning biomass,
$\hat{a}$ is selectivity-at-age-50%, and
$\hat{\gamma}$ is selectivity standard deviation-at-50%.
Subscripts on $\hat{a}$ and $\hat{\gamma}$ represent gears as follows:
1 represents the reduction, the food and bait, as well as the special use fishery,
2 represents the roe gillnet fishery, and
3 represents the roe seine fishery.

(ref:hg-traces-cap-fr) Tracés des résultats de simulation
Monte Carlo par chaîne de Markov pour les paramètres estimés
pour le hareng du Pacifique
dans la région d’évaluation des stocks majeur de Haida Gwaii.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}
pour la description.
De plus, $\SB_0$ est la biomasse non exploitée estimée,
$\SB_0$ est la biomasse reproductrice non exploitée estimée,
$\SB$ est la biomasse reproductrice,
$\hat{a}$ est sélectivité selon l’âge à 50%, et
$\hat{\gamma}$ est écart-type de la sélectivité selon l’âge à 50%.
Les souscriptions sur $\hat{a}$ et $\hat{\gamma}$ représentent
des engins comme suit:
1 représente la réduction, ainsi que les pêches pratiquées à des fins
de subsistance, pour le marché des appâts et pour des usages spéciaux, 
2 représente la pêche au hareng rogué au filet maillant, et
3 représente la pêche au hareng rogué à la senne.

```{r hg-traces, fig.asp=1, fig.cap=ifelse(french, "(ref:hg-traces-cap-fr)", "(ref:hg-traces-cap)")}
make.traces.plot(
  model = major_models[[model_ind]], mcmc_burnin = mcmc_burnin
)
```

(ref:hg-autocor-cap) Haida Gwaii SAR:
autocorrelation plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables}, and
Figure \@ref(fig:hg-traces) for description.

(ref:hg-autocor-cap-fr) Diagrammes d’autocorrélation des résultats
de simulation Monte Carlo par chaîne de Markov pour les
paramètres estimés pour le hareng du Pacifique
dans la région d’évaluation des stocks majeur de Haida Gwaii.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}, et
la figure \@ref(fig:hg-traces) pour la description.

```{r hg-autocor, fig.asp=1, fig.cap=ifelse(french, "(ref:hg-autocor-cap-fr)", "(ref:hg-autocor-cap)")}
make.autocor.plot(
  model = major_models[[model_ind]], mcmc_burnin = mcmc_burnin
)
```

(ref:hg-pairs-cap) Haida Gwaii SAR:
pairs plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables}, and
Figure \@ref(fig:hg-traces) for description.

(ref:hg-pairs-cap-fr) Diagrammes par paires des résultats
de simulation Monte Carlo par chaîne de Markov pour
les paramètres estimés pour le hareng du Pacifique
dans la region d’évaluation des stocks majeur de Haida Gwaii.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}, et
la figure \@ref(fig:hg-traces) pour la description.

```{r hg-pairs, fig.asp=1, fig.cap=ifelse(french, "(ref:hg-pairs-cap-fr)", "(ref:hg-pairs-cap)")}
make.pairs.plot(
  model = major_models[[model_ind]],
  params = c(
    "ro", "h", "m", "rbar", "rinit", "q1", "q2", "sel1", "selsd1", "sel2",
    "selsd2", "sel3", "selsd3"
  )
)
```

(ref:hg-biomass-retro-cap) Haida Gwaii SAR:
maximum posterior density (MPD)
of spawning biomass in thousands of tonnes (t; lines)
from `r new_surv_yr` to `r assess_yr` (base model) with retrospectives 
(-`r min(retro_yrs)` to -`r max(retro_yrs)` years)
for the Pacific Herring statistical catch-age model.
Points indicate MPD of long-term estimated unfished spawning biomass.
Triangles indicate scaled abundance.

(ref:hg-biomass-retro-cap-fr) Densité a posteriori maximale (DPM)
de la biomasse reproductrice en milliers de tonnes (t; lignes)
de `r new_surv_yr` à `r assess_yr` (modèle de base) avec des rétrospectives
(-`r min(retro_yrs)` à -`r max(retro_yrs)` années)
pour le hareng du Pacifique dans la
région d'évaluation des stocks majeur de Haida Gwaii.
Les points indiquent la DPM de la biomasse reporductrice non exploitée estimée
à long terme.
Les triangles indiquent l'abondance à l'échelle.

```{r hg-biomass-retro, fig.asp=0.65, fig.cap=ifelse(french, "(ref:hg-biomass-retro-cap-fr)", "(ref:hg-biomass-retro-cap)")}
biomass.plot.mpd(
  model = major_models[[model_ind]],
  xlim = c(new_surv_yr, assess_yr),
  df = major_surv %>% filter(region == major_regions_full[model_ind]),
  translate = french
)
```

(ref:hg-sr-cap) Haida Gwaii SAR:
relationship between spawning biomass in thousands of tonnes (t) and
the number of age-`r age_first` recruits in thousands of millions (points),
as well as the predicted Beverton-Holt stock-recruitment relationship (line)
for the Pacific Herring statistical catch-age model.
The star indicates unfished spawning biomass and
unfished age-`r age_first` recruitment.
Shading becomes darker in chronological order;
the triangle indicates `r assess_yr`.
Note: values are median posterior estimates.

(ref:hg-sr-cap-fr) La relation entre la biomasse reproductrice
en milliers de tonnes (t) et
le nombre de recrues d'âge `r age_first` en milliers de millions (points),
ainsi que la relation stock-recrutement
du modèle Beverton-Holt prévue (ligne)
pour le hareng du Pacifique
dans la région d'évaluation des stocks majeur de Haida Gwaii.
L'étoile indique la biomasse du stock reproducteur non exploitée et
le recrutement de l’âge `r age_first` dans le stock non exploité.
L’ombrage est de plus en plus foncé à mesure que l’on avance
dans la série chronologique;
le triangle indique `r assess_yr`.
Remarque: les valeurs sont des estimations médianes postérieures.

```{r hg-sr, fig.asp=0.4, fig.cap=ifelse(french, "(ref:hg-sr-cap-fr)", "(ref:hg-sr-cap)")}
plot_bh(
  model = major_models[[model_ind]],
  regions = major_regions_full[[model_ind]],
  translate = french
)
```
