\clearpage

# Prince Rupert District diagnostics

This section contains Markov chain Monte Carlo (MCMC) diagnostics
for the Pacific Herring statistical catch-age model
in the Prince Rupert District major stock assessment region.
The MCMC run had chain length `r number_to_word(mcmc_length)`
with a sample taken every `r number_to_word(mcmc_samp_freq)` iterations
(i.e., thinning).
The first `r number_to_word(mcmc_burnin)` samples were discarded (i.e., burn-in),
leaving `r number_to_word(mcmc_num_samples)` samples for posteriors.
This section will not be included in the final document.

Autocorrelation was detected within a number of the parameters. Inline with procedures used on WCVI parameter priors were reparameterized. For logarithmic natural mortality the upper bound was reduced from 5 to 3, and the mean was shifted from -0.8 to -0.5. For logarithmic initial recruitment the uniform prior was changed to a normal distribution with mean 5 and a sd of 3. For logarithmic average recruitment the uniform prior was changed to a normal distribution with mean 5 and sd 5. The sd for selectivity for gear 3 [TODO: insert geartype name]was widened from 0.25 to 0.5. For the logarithmic catchability quotient for surface surveys the uniform prior was changed to a normal distribution with mean 0 and sd 1. 

(ref:prd-priors-posts-cap) Prince Rupert District SAR:
prior probability distributions (lines) with
comparative posterior histograms (bars)
for the Pacific Herring statistical catch-age model.
See Table \@ref(tab:hg-parameter-est) and
Figure \@ref(fig:hg-priors-posts) for description.

(ref:prd-priors-posts-cap-fr) Distributions de probabilité a priori (lignes)
et histogrammes a posteriori comparatifs (barres)
pour le hareng du Pacifique dans la région d’évaluation des stocks
majeur du district de Prince Rupert.
Voir le tableau \@ref(tab:hg-parameter-est) et la
figure \@ref(fig:hg-priors-posts) pour la description.

```{r prd-priors-posts, fig.cap=ifelse(french, "(ref:prd-priors-posts-cap-fr)", "(ref:prd-priors-posts-cap)")}
model_ind <- match(en2fr("PRD", french), major_regions_short)
make.priors.posts.plot(
  model = major_models[[model_ind]],
  priors.only = FALSE
)
```

(ref:prd-traces-cap) Prince Rupert District SAR:
trace plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables}, and
Figure \@ref(fig:hg-traces) for description.

(ref:prd-traces-cap-fr) Tracés des résultats de simulation
Monte Carlo par chaîne de Markov pour les paramètres estimés
pour le hareng du Pacifique dans la région d’évaluation des stocks
majeur du district de Prince Rupert.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}, et
la figure \@ref(fig:hg-traces) pour la description.

```{r prd-traces, fig.asp=1, fig.cap=ifelse(french, "(ref:prd-traces-cap-fr)", "(ref:prd-traces-cap)")}
make.traces.plot(
  model = major_models[[model_ind]], mcmc_burnin = mcmc_burnin
)
```

(ref:prd-autocor-cap) Prince Rupert District SAR:
autocorrelation plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables}, and
Figure \@ref(fig:hg-traces) for description.

(ref:prd-autocor-cap-fr) Diagrammes d’autocorrélation des résultats
de simulation Monte Carlo par chaîne de Markov
pour les paramètres estimés pour le hareng du Pacifique dans
la région d’évaluation des stocks majeur du district de Prince Rupert.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}, et
la figure \@ref(fig:hg-traces) pour la description.

```{r prd-autocor, fig.asp=1, fig.cap=ifelse(french, "(ref:prd-autocor-cap-fr)", "(ref:prd-autocor-cap)")}
make.autocor.plot(
  model = major_models[[model_ind]], mcmc_burnin = mcmc_burnin
)
```

(ref:prd-pairs-cap) Prince Rupert District SAR:
pairs plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables}, and
Figure \@ref(fig:hg-traces) for description.

(ref:prd-pairs-cap-fr) Diagrammes par paires des résultats de simulation
Monte Carlo par chaîne de Markov pour
les paramètres estimés pour le hareng du Pacifique
dans la region d’évaluation des stocks majeur du district de Prince Rupert.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}, et
la figure \@ref(fig:hg-traces) pour la description.

```{r prd-pairs, fig.asp=1, fig.cap=ifelse(french, "(ref:prd-pairs-cap-fr)", "(ref:prd-pairs-cap)")}
make.pairs.plot(
  model = major_models[[model_ind]],
  params = c(
    "ro", "h", "m", "rbar", "rinit", "q1", "q2", "sel1", "selsd1", "sel2",
    "selsd2", "sel3", "selsd3"
  )
)
```

(ref:prd-biomass-retro-cap) Prince Rupert District SAR:
maximum posterior density (MPD) 
of spawning biomass in thousands of tonnes (t; lines)
from `r new_surv_yr` to `r assess_yr` (base model) with retrospectives 
(-`r min(retro_yrs)` to -`r max(retro_yrs)` years)
for the Pacific Herring statistical catch-age model.
See Figure \@ref(fig:hg-biomass-retro) for description.

(ref:prd-biomass-retro-cap-fr) Densité a posteriori maximale (DPM)
de la biomasse reproductrice en milliers de tonnes (t; lignes)
de `r new_surv_yr` à `r assess_yr` (modèle de base) avec des rétrospectives
(-`r min(retro_yrs)` à -`r max(retro_yrs)` années)
pour le hareng du Pacifique dans la
région d'évaluation des stocks majeur du district de Prince Rupert.
Voir la figure \@ref(fig:hg-biomass-retro) pour la description.

```{r prd-biomass-retro, fig.asp=0.65, fig.cap=ifelse(french, "(ref:prd-biomass-retro-cap-fr)", "(ref:prd-biomass-retro-cap)")}
biomass.plot.mpd(
  model = major_models[[model_ind]],
  xlim = c(new_surv_yr, assess_yr),
  df = major_surv %>% filter(region == major_regions_full[model_ind]),
  translate = french
)
```

(ref:prd-sr-cap) Prince Rupert Distric SAR:
relationship between spawning biomass in thousands of tonnes (t) and
the number of age-`r age_first` recruits in thousands of millions (points),
as well as the predicted Beverton-Holt stock-recruitment relationship (line)
for the Pacific Herring statistical catch-age model.
See Figure \@ref(fig:hg-sr) for description.

(ref:prd-sr-cap-fr) La relation entre la biomasse reproductrice
en milliers de tonnes (t) et
le nombre de recrues d'âge `r age_first` en milliers de millions (points),
ainsi que la relation stock-recrutement du modèle Beverton-Holt prévue (ligne)
pour le hareng du Pacifique
dans la région d'évaluation des stocks majeur du district de Prince Rupert.
Voir la figure \@ref(fig:hg-sr) pour la description.

```{r prd-sr, fig.asp=0.4, fig.cap=ifelse(french, "(ref:prd-sr-cap-fr)", "(ref:prd-sr-cap)")}
plot_bh(
  model = major_models[[model_ind]],
  regions = major_regions_full[[model_ind]],
  translate = french
)
```

(ref:hcr-prd-cap) Prince Rupert District SAR: relationships between
projected depletion in `r assess_yr + 1` $\SB_{`r assess_yr+1`}/\SB_0$,
harvest rate (HR), and total allowable catch (TAC) for
management procedures (MPs) in Table \@ref(tab:decision-prd).
There are four panels fo each MP arranged in a 2x2 grid:
the top-right panel has the MP name and
the other three panels show relationships.
Note: figure excludes MPs that specify no fishing, and
panels are the same for both operating model scenarios.
Red lines show median depletion, HR, and TAC;
green lines show means.

```{r hcr-prd, fig.asp=1, fig.cap="(ref:hcr-prd-cap)", eval=TRUE}
region <- "PRD"
cowplot::plot_grid(
  plot_hcr(
    hcr.lst = mp.lst.prd[[1]][[2]],
    sbt.lst = sbt.prd,
    sbo.lst = sbo.prd,
    mp = mp.prd[2, ]$label,
    region = region,
    probs = confidence_vals
  ),
  plot_hcr(
    hcr.lst = mp.lst.prd[[1]][[3]],
    sbt.lst = sbt.prd,
    sbo.lst = sbo.prd,
    mp = mp.prd[3, ]$label,
    region = region,
    probs = confidence_vals
  ),
  plot_hcr(
    hcr.lst = mp.lst.prd[[1]][[4]],
    sbt.lst = sbt.prd,
    sbo.lst = sbo.prd,
    mp = mp.prd[4, ]$label,
    region = region,
    probs = confidence_vals
  ),
  plot_hcr(
    hcr.lst = mp.lst.prd[[1]][[5]],
    sbt.lst = sbt.prd,
    sbo.lst = sbo.prd,
    mp = mp.prd[5, ]$label,
    region = region,
    probs = confidence_vals
  ),
  plot_hcr(
    hcr.lst = mp.lst.prd[[1]][[6]],
    sbt.lst = sbt.prd,
    sbo.lst = sbo.prd,
    mp = mp.prd[6, ]$label,
    region = region,
    probs = confidence_vals
  ),
  plot_hcr(
    hcr.lst = mp.lst.prd[[1]][[7]],
    sbt.lst = sbt.prd,
    sbo.lst = sbo.prd,
    mp = mp.prd[7, ]$label,
    region = region,
    probs = confidence_vals
  ),
  nrow = 3,
  ncol = 2,
  align = "hv",
  axis = "tblr"
)
```
