# Prince Rupert District diagnostics

This section contains Markov chain Monte Carlo (MCMC) diagnostics for the Pacific Herring statistical catch-age model
in the Prince Rupert District major stock assessment region.
The MCMC run had chain length `r mcmc_length`
with a sample taken every `r f(mcmc_samp_freq)`^th^ iteration (i.e., thinning).
The first `r f(mcmc_burnin)` samples were discarded (i.e., burn-in),
leaving `r f(mcmc_num_samples)` samples for posteriors.
This section will not be included in the final document.

(ref:prd-priors-posts-cap) Prince Rupert District SAR:
prior probability distributions (lines) with
comparative posterior histograms (bars)
for the Pacific Herring statistical catch-age model.
See Table \@ref(tab:hg-parameter-est) and Figure \@ref(fig:hg-priors-posts) for description.

(ref:prd-priors-posts-cap-fr) Distributions de probabilité a priori (lignes)
et histogrammes a posteriori comparatifs (barres) pour le hareng du Pacifique dans la région d’évaluation des stocks majeur du district de Prince Rupert.
Voir le tableau \@ref(tab:hg-parameter-est) et la figure \@ref(fig:hg-priors-posts) pour la description.

```{r prd-priors-posts, fig.cap=ifelse(french, "(ref:prd-priors-posts-cap-fr)", "(ref:prd-priors-posts-cap)")}
model_ind <- match(en2fr("PRD", french), major_regions_short)
make.priors.posts.plot(
  model = major_models[[model_ind]],
  priors.only = FALSE
)
```

(ref:prd-traces-cap) Prince Rupert District SAR:
trace plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables}, and Figure \@ref(fig:hg-traces) for description.

(ref:prd-traces-cap-fr) Tracés des résultats de simulation Monte Carlo par chaîne de Markov pour les paramètres estimés pour le hareng du Pacifique
dans la région d’évaluation des stocks majeur du district de Prince Rupert.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}, et la figure \@ref(fig:hg-traces) pour la description.

```{r prd-traces, fig.asp=1, fig.cap=ifelse(french, "(ref:prd-traces-cap-fr)", "(ref:prd-traces-cap)")}
make.traces.plot(
  model = major_models[[model_ind]], mcmc_burnin = mcmc_burnin
)
```

(ref:prd-autocor-cap) Prince Rupert District SAR:
autocorrelation plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables}, and Figure \@ref(fig:hg-traces) for description.

(ref:prd-autocor-cap-fr) Diagrammes d’autocorrélation des résultats de simulation Monte Carlo par chaîne de Markov pour les paramètres estimés pour le hareng du Pacifique dans la région d’évaluation des stocks majeur du district de Prince Rupert.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}, et la figure \@ref(fig:hg-traces) pour la description.

```{r prd-autocor, fig.asp=1, fig.cap=ifelse(french, "(ref:prd-autocor-cap-fr)", "(ref:prd-autocor-cap)")}
make.autocor.plot(
  model = major_models[[model_ind]], mcmc_burnin = mcmc_burnin
)
```

(ref:prd-pairs-cap) Prince Rupert District SAR:
pairs plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables}, and Figure \@ref(fig:hg-traces) for description.

(ref:prd-pairs-cap-fr) Diagrammes par paires des résultats de simulation Monte Carlo par chaîne de Markov pour
les paramètres estimés pour le hareng du Pacifique dans la region d’évaluation des stocks majeur du district de Prince Rupert.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}, et la figure \@ref(fig:hg-traces) pour la description.

```{r prd-pairs, fig.asp=1, fig.cap=ifelse(french, "(ref:prd-pairs-cap-fr)", "(ref:prd-pairs-cap)")}
make.pairs.plot(
  model = major_models[[model_ind]],
  params = c(
    "ro", "h", "m", "rbar", "rinit", "q1", "q2", "sel1", "selsd1", "sel2",
    "selsd2", "sel3", "selsd3"
  )
)
```

(ref:prd-biomass-retro-cap) Prince Rupert District SAR:
maximum posterior density of spawning biomass in thousands of tonnes (t; lines)
from `r new_surv_yr` to `r assess_yr` (base model) with retrospectives 
(-`r min(retro_yrs)` to -`r max(retro_yrs)` years)
for the Pacific Herring statistical catch-age model.
See Figure \@ref(fig:hg-biomass-retro) for description.

(ref:prd-biomass-retro-cap-fr) Densité a posteriori maximale de la biomasse reproductrice en milliers de tonnes (t; lignes)
de `r new_surv_yr` à `r assess_yr` (modèle de base) avec des rétrospectives
(-`r min(retro_yrs)` à -`r max(retro_yrs)` années)
pour le hareng du Pacifique dans la
région d'évaluation des stocks majeur du district de Prince Rupert.
Voir la figure \@ref(fig:hg-biomass-retro) pour la description.

```{r prd-biomass-retro, fig.asp=0.65, fig.cap=ifelse(french, "(ref:prd-biomass-retro-cap-fr)", "(ref:prd-biomass-retro-cap)")}
biomass.plot.mpd(
  model = major_models[[model_ind]],
  xlim = c(new_surv_yr, assess_yr),
  df = major_surv %>% filter(region == major_regions_full[model_ind]),
  translate = french
)
```

(ref:prd-sr-cap) Prince Rupert Distric SAR:
relationship between spawning biomass in thousands of tonnes (t) and
the number of age-`r age_first` recruits in thousands of millions (points),
as well as the predicted Beverton-Holt stock-recruitment relationship (line)
for the Pacific Herring statistical catch-age model.
See Figure \@ref(fig:hg-sr) for description.

(ref:prd-sr-cap-fr) La relation entre la biomasse reproductrice en milliers de tonnes (t) et
le nombre de recrues d'âge `r age_first` en milliers de millions (points), ainsi que
la relation stock-recrutement du modèle Beverton-Holt prévue (ligne)
pour le hareng du Pacifique dans la région d'évaluation des stocks majeur du district de Prince Rupert.
Voir la figure \@ref(fig:hg-sr) pour la description.

```{r prd-sr, fig.asp=0.4, fig.cap=ifelse(french, "(ref:prd-sr-cap-fr)", "(ref:prd-sr-cap)")}
plot_bh(
  model = major_models[[model_ind]],
  regions = major_regions_full[[model_ind]],
  translate = french
)
```

(ref:hcr-prd-cap) Prince Rupert District SAR:
projected spawning biomass for `r assess_yr + 1` $\SB_{`r assess_yr+1`}$
compared to harvest rate (HR) and total allowable catch (TAC)
(rows 1 to 4 in Table \@ref(tab:decision-prd)).
Red horizontal and vertical lines show median HR, TAC, and $\SB_{`r assess_yr+1`}$;
green lines show mean statistics.

```{r hcr-prd, fig.asp=0.75, fig.cap="(ref:hcr-prd-cap)"}
region <- "PRD"
probs <- confidence_vals
cowplot::plot_grid(
  plot_hcr(
    hcr.lst = mp.lst.prd[[1]][[1]],
    sbt.lst = sbt.prd,
    mp = mp.prd[1, ]$label,
    region = region,
    probs = probs
  ),
  plot_hcr(
    hcr.lst = mp.lst.prd[[1]][[2]],
    sbt.lst = sbt.prd,
    mp = mp.prd[2, ]$label,
    region = region,
    probs = probs
  ),
  plot_hcr(
    hcr.lst = mp.lst.prd[[1]][[3]],
    sbt.lst = sbt.prd,
    mp = mp.prd[3, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  plot_hcr(
    mp.lst.prd[[1]][[4]],
    sbt.prd,
    mp = mp.prd[4, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  nrow = 2,
  ncol = 2,
  align = "hv",
  axis = "tblr"
)
```

(ref:hcr-prd-2-cap) Prince Rupert District SAR:
projected spawning biomass for `r assess_yr + 1` $\SB_{`r assess_yr+1`}$
compared to harvest rate (HR) and total allowable catch (TAC)
(rows 5 to 8 in Table \@ref(tab:decision-prd)).
See Figure \@ref(fig:hcr-prd) for description.

```{r hcr-prd-2, fig.asp=0.75, fig.cap="(ref:hcr-prd-2-cap)"}
region <- "PRD"
probs <- confidence_vals
cowplot::plot_grid(
  plot_hcr(
    hcr.lst = mp.lst.prd[[1]][[5]],
    sbt.lst = sbt.prd,
    mp = mp.prd[5, ]$label,
    region = region,
    probs = probs
  ),
  plot_hcr(
    hcr.lst = mp.lst.prd[[1]][[6]],
    sbt.lst = sbt.prd,
    mp = mp.prd[6, ]$label,
    region = region,
    probs = probs
  ),
  plot_hcr(
    hcr.lst = mp.lst.prd[[1]][[7]],
    sbt.lst = sbt.prd,
    mp = mp.prd[7, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  plot_hcr(
    hcr.lst = mp.lst.prd[[1]][[8]],
    sbt.lst = sbt.prd,
    mp = mp.prd[8, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  nrow = 2,
  ncol = 2,
  align = c("v", "h")
)
```

(ref:hcr-prd-3-cap) Prince Rupert District SAR:
projected spawning biomass for `r assess_yr + 1` $\SB_{`r assess_yr+1`}$
compared to harvest rate (HR) and total allowable catch (TAC)
(rows 9 to 10 in Table \@ref(tab:decision-prd)).
See Figure \@ref(fig:hcr-prd) for description.

```{r hcr-prd-3, fig.asp=0.75, fig.cap="(ref:hcr-prd-3-cap)"}
region <- "PRD"
probs <- confidence_vals
cowplot::plot_grid(
  plot_hcr(
    hcr.lst = mp.lst.prd[[1]][[9]],
    sbt.lst = sbt.prd,
    mp = mp.prd[9, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  plot_hcr(
    hcr.lst = mp.lst.prd[[1]][[10]],
    sbt.lst = sbt.prd,
    mp = mp.prd[10, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  nrow = 2,
  ncol = 1,
  align = c("v", "h")
)
```
