\clearpage

# Strait of Georgia diagnostics

This section contains Markov chain Monte Carlo (MCMC) diagnostics
for the Pacific Herring statistical catch-age model
in the Strait of Georgia major stock assessment region.
The MCMC run had chain length `r number_to_word(mcmc_length)`
with a sample taken every `r number_to_word(mcmc_samp_freq)` iterations
(i.e., thinning).
The first `r number_to_word(mcmc_burnin)` samples were discarded (i.e., burn-in),
leaving `r number_to_word(mcmc_num_samples)` samples for posteriors.
This section will not be included in the final document.

(ref:sog-priors-posts-cap) Strait of Georgia SAR:
prior probability distributions (lines) with
comparative posterior histograms (bars)
for the Pacific Herring statistical catch-age model.
See Table \@ref(tab:hg-parameter-est) and
Figure \@ref(fig:hg-priors-posts) for description.

(ref:sog-priors-posts-cap-fr) Distributions de probabilité a priori (lignes)
et histogrammes a posteriori comparatifs (barres)
pour le hareng du Pacifique
dans la région d’évaluation des stocks majeur du détroit de Georgie.
Voir le tableau \@ref(tab:hg-parameter-est) et
la figure \@ref(fig:hg-priors-posts) pour la description.

```{r sog-priors-posts, fig.cap=ifelse(french, "(ref:sog-priors-posts-cap-fr)", "(ref:sog-priors-posts-cap)")}
model_ind <- match(en2fr("SoG", french), major_regions_short)
make.priors.posts.plot(
  model = major_models[[model_ind]],
  priors.only = FALSE
)
```

(ref:sog-traces-cap) Strait of Georgia SAR:
trace plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables}, and
Figure \@ref(fig:hg-traces) for description.

(ref:sog-traces-cap-fr) Tracés des résultats de simulation
Monte Carlo par chaîne de Markov pour les paramètres estimés
pour le hareng du Pacifique
dans la région d’évaluation des stocks majeur du détroit de Georgie.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}, et
la figure \@ref(fig:hg-traces) pour la description.

```{r sog-traces, fig.asp=1, fig.cap=ifelse(french, "(ref:sog-traces-cap-fr)", "(ref:sog-traces-cap)")}
make.traces.plot(
  model = major_models[[model_ind]], mcmc_burnin = mcmc_burnin
)
```

(ref:sog-autocor-cap) Strait of Georgia SAR:
autocorrelation plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables}, and
Figure \@ref(fig:hg-traces) for description.

(ref:sog-autocor-cap-fr) Diagrammes d’autocorrélation des résultats de
simulation Monte Carlo par chaîne de Markov pour les
paramètres estimés pour le hareng du Pacifique
dans la région d’évaluation des stocks majeur du détroit de Georgie.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}, et
la figure \@ref(fig:hg-traces) pour la description.

```{r sog-autocor, fig.asp=1, fig.cap=ifelse(french, "(ref:sog-autocor-cap-fr)", "(ref:sog-autocor-cap)")}
make.autocor.plot(
  model = major_models[[model_ind]], mcmc_burnin = mcmc_burnin
)
```

(ref:sog-pairs-cap) Strait of Georgia SAR:
pairs plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables}, and
Figure \@ref(fig:hg-traces) for description.

(ref:sog-pairs-cap-fr) Diagrammes par paires des résultats de
simulation Monte Carlo par chaîne de Markov pour
les paramètres estimés pour le hareng du Pacifique
dans la region d’évaluation des stocks majeur du détroit de Georgie.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}, et
la figure \@ref(fig:hg-traces) pour la description.

```{r sog-pairs, fig.asp=1, fig.cap=ifelse(french, "(ref:sog-pairs-cap-fr)", "(ref:sog-pairs-cap)")}
make.pairs.plot(
  model = major_models[[model_ind]],
  params = c(
    "ro", "h", "m", "rbar", "rinit", "q1", "q2", "sel1", "selsd1", "sel2",
    "selsd2", "sel3", "selsd3"
  )
)
```

(ref:sog-biomass-retro-cap) Strait of Georgia SAR:
maximum posterior density (MPD)
of spawning biomass in thousands of tonnes (t; lines)
from `r new_surv_yr` to `r assess_yr` (base model) with retrospectives 
(-`r min(retro_yrs)` to -`r max(retro_yrs)` years)
for the Pacific Herring statistical catch-age model.
See Figure \@ref(fig:hg-biomass-retro) for description.

(ref:sog-biomass-retro-cap-fr) Densité a posteriori maximale (DPM)
de la biomasse reproductrice en milliers de tonnes (t; lignes)
de `r new_surv_yr` à `r assess_yr` (modèle de base) avec des rétrospectives
(-`r min(retro_yrs)` à -`r max(retro_yrs)` années)
pour le hareng du Pacifique dans la
région d'évaluation des stocks majeur du détroit de Georgie.
Voir la figure \@ref(fig:hg-biomass-retro) pour la description.

```{r sog-biomass-retro, fig.asp=0.65, fig.cap=ifelse(french, "(ref:sog-biomass-retro-cap-fr)", "(ref:sog-biomass-retro-cap)")}
biomass.plot.mpd(
  model = major_models[[model_ind]],
  xlim = c(new_surv_yr, assess_yr),
  df = major_surv %>% filter(region == major_regions_full[model_ind]),
  translate = french
)
```

(ref:sog-sr-cap) Strait of Georgia SAR:
relationship between spawning biomass in thousands of tonnes (t) and
the number of age-`r age_first` recruits in thousands of millions (points),
as well as the predicted Beverton-Holt stock-recruitment relationship (line)
for the Pacific Herring statistical catch-age model.
See Figure \@ref(fig:hg-sr) for description.

(ref:sog-sr-cap-fr) La relation entre la biomasse reproductrice
en milliers de tonnes (t) et
le nombre de recrues d'âge `r age_first` en milliers de millions (points),
ainsi que la relation stock-recrutement du modèle Beverton-Holt prévue (ligne)
pour le hareng du Pacifique
dans la région d’évaluation des stocks majeur du détroit de Georgie.
Voir la figure \@ref(fig:hg-sr) pour la description.

```{r sog-sr, fig.asp=0.4, fig.cap=ifelse(french, "(ref:sog-sr-cap-fr)", "(ref:sog-sr-cap)")}
plot_bh(
  model = major_models[[model_ind]],
  regions = major_regions_full[[model_ind]],
  translate = french
)
```

(ref:hcr-sog-1-cap) Strait of Georgia SAR:
projected spawning biomass for `r assess_yr + 1` $\SB_{`r assess_yr+1`}$
compared to harvest rate (HR) and total allowable catch (TAC;
rows 2 to 7 in Table \@ref(tab:decision-sog)).
See Figure \@ref(fig:hcr-prd-1) for description.

```{r hcr-sog-1, fig.asp=1, fig.cap="(ref:hcr-sog-1-cap)", eval=TRUE}
region <- "SoG"
probs <- confidence_vals
cowplot::plot_grid(
  plot_hcr(
    hcr.lst = mp.lst.sog[[1]][[2]],
    sbt.lst = sbt.sog,
    sbo.lst = sbo.sog,
    mp = mp.sog[2, ]$label,
    region = region,
    probs = probs
  ),
  plot_hcr(
    hcr.lst = mp.lst.sog[[1]][[3]],
    sbt.lst = sbt.sog,
    sbo.lst = sbo.sog,
    mp = mp.sog[3, ]$label,
    region = region,
    probs = probs
  ),
  plot_hcr(
    hcr.lst = mp.lst.sog[[1]][[4]],
    sbt.lst = sbt.sog,
    sbo.lst = sbo.sog,
    mp = mp.sog[4, ]$label,
    region = region,
    probs = probs
  ),
  plot_hcr(
    hcr.lst = mp.lst.sog[[1]][[5]],
    sbt.lst = sbt.sog,
    sbo.lst = sbo.sog,
    mp = mp.sog[5, ]$label,
    region = region,
    probs = probs
  ),
  plot_hcr(
    hcr.lst = mp.lst.sog[[1]][[6]],
    sbt.lst = sbt.sog,
    sbo.lst = sbo.sog,
    mp = mp.sog[6, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  plot_hcr(
    hcr.lst = mp.lst.sog[[1]][[7]],
    sbt.lst = sbt.sog,
    sbo.lst = sbo.sog,
    mp = mp.sog[7, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  nrow = 3,
  ncol = 2,
  align = "hv",
  axis = "tblr"
)
```

(ref:hcr-sog-2-cap) Strait of Georgia SAR:
projected spawning biomass for `r assess_yr + 1` $\SB_{`r assess_yr+1`}$
compared to harvest rate (HR) and total allowable catch (TAC;
rows 9 to 14 in Table \@ref(tab:decision-sog)).
See Figure \@ref(fig:hcr-prd-1) for description.

```{r hcr-sog-2, fig.asp=1, fig.cap="(ref:hcr-sog-2-cap)", eval=TRUE}
region <- "SoG"
probs <- confidence_vals
cowplot::plot_grid(
  plot_hcr(
    hcr.lst = mp.lst.sog[[1]][[9]],
    sbt.lst = sbt.sog,
    sbo.lst = sbo.sog,
    mp = mp.sog[9, ]$label,
    region = region,
    probs = probs
  ),
  plot_hcr(
    hcr.lst = mp.lst.sog[[1]][[10]],
    sbt.lst = sbt.sog,
    sbo.lst = sbo.sog,
    mp = mp.sog[10, ]$label,
    region = region,
    probs = probs
  ),
  plot_hcr(
    hcr.lst = mp.lst.sog[[1]][[11]],
    sbt.lst = sbt.sog,
    sbo.lst = sbo.sog,
    mp = mp.sog[11, ]$label,
    region = region,
    probs = probs
  ),
  plot_hcr(
    hcr.lst = mp.lst.sog[[1]][[12]],
    sbt.lst = sbt.sog,
    sbo.lst = sbo.sog,
    mp = mp.sog[12, ]$label,
    region = region,
    probs = probs
  ),
  plot_hcr(
    hcr.lst = mp.lst.sog[[1]][[13]],
    sbt.lst = sbt.sog,
    sbo.lst = sbo.sog,
    mp = mp.sog[13, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  plot_hcr(
    hcr.lst = mp.lst.sog[[1]][[14]],
    sbt.lst = sbt.sog,
    sbo.lst = sbo.sog,
    mp = mp.sog[14, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  nrow = 3,
  ncol = 2,
  align = c("v", "h")
)
```
