# West Coast of Vancouver Island diagnostics

This section contains Markov chain Monte Carlo (MCMC) diagnostics for the Pacific Herring statistical catch-age model
in the West Coast of Vancouver Island major stock assessment region.
The MCMC run had chain length `r mcmc_length`
with a sample taken every `r f(mcmc_samp_freq)`^th^ iteration (i.e., thinning).
The first `r f(mcmc_burnin)` samples were discarded (i.e., burn-in),
leaving `r f(mcmc_num_samples-mcmc_burnin)` samples for posteriors.
This section will not be included in the final document.

Autocorrelation was detected in the MCMC iterations for both
the reduction fisheries selectivity-at-50% ($\hat{a}_{1}$) and
its standard deviation ($\hat{\gamma}_{1}$) for the WCVI SAR.
For the WCVI, we attempted to reduce autocorrelation by
using posterior medians from last year as starting values,
increasing the MCMC chain from 5 million to 10 million iterations, and
increasing the burn-in from 1,000 to 5,000, and then again to 7,000.
The thinning rate, choosing 1 out of every 1,000 was kept the same.
The autocorrelation for both $\hat{a}_{1}$ and $\hat{\gamma}_{1}$
was reduced but still persistent.
We attempted to run the chain for 20 million iterations with a 1 in 4,000 thin rate,
but was not successful due to computing limitations.
Since these attempts were not more successful,
we reported the results of the 5 million-run chain to be consistent with other SARs.

Autocorrelation in MCMC iterations may indicate bias in posterior distributions.
Autocorrelation could be caused by not having enough data,
which could be the case because the WCVI SAR
has been closed to commercial fishing since 2005.
When fisheries open, more data could help inform the model
to reduce autocorrelation and resulting bias.
<!-- TODO: Not sure we want to include this last sentence? -->
Since the fishery is currently closed, we accept that bias may be present, and
focus computing and personnel resources toward other matters.

(ref:wcvi-priors-posts-cap) West Coast of Vancouver Island SAR:
prior probability distributions (lines) with
comparative posterior histograms (bars)
for the Pacific Herring statistical catch-age model.
See Table \@ref(tab:hg-parameter-est) and Figure \@ref(fig:hg-priors-posts) for description.

(ref:wcvi-priors-posts-cap-fr) Distributions de probabilité a priori (lignes)
et histogrammes a posteriori comparatifs (barres) pour le hareng du Pacifique dans la région d’évaluation des stocks majeur de la côte ouest de l’île de Vancouver.
Voir le tableau \@ref(tab:hg-parameter-est) et la figure \@ref(fig:hg-priors-posts) pour la description.

```{r wcvi-priors-posts, fig.cap=ifelse(french, "(ref:wcvi-priors-posts-cap-fr)", "(ref:wcvi-priors-posts-cap)")}
model_ind <- match(en2fr("WCVI", french), major_regions_short)
make.priors.posts.plot(major_models[[model_ind]],
                       priors.only = FALSE)
```

(ref:wcvi-traces-cap) West Coast of Vancouver Island SAR:
trace plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables}, and Figure \@ref(fig:hg-traces) for description.

(ref:wcvi-traces-cap-fr) Tracés des résultats de simulation Monte Carlo par chaîne de Markov pour les paramètres estimés pour le hareng du Pacifique
dans la région d’évaluation des stocks majeur de la côte ouest de l’île de Vancouver.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}, et la figure \@ref(fig:hg-traces) pour la description.

```{r wcvi-traces, fig.asp=1, fig.cap=ifelse(french, "(ref:wcvi-traces-cap-fr)", "(ref:wcvi-traces-cap)")}
make.traces.plot(major_models[[model_ind]], 
                 mcmc_burnin = 1000, #not sure about this burnin
                 axis.lab.freq = 200)
```

(ref:wcvi-autocor-cap) West Coast of Vancouver Island SAR:
autocorrelation plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables}, and Figure \@ref(fig:hg-traces) for description.

(ref:wcvi-autocor-cap-fr) Diagrammes d’autocorrélation des résultats de simulation Monte Carlo par chaîne de Markov pour les
paramètres estimés pour le hareng du Pacifique dans la région d’évaluation des stocks majeur de la côte ouest de l’île de Vancouver.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}, et la figure \@ref(fig:hg-traces) pour la description.

```{r wcvi-autocor, fig.asp=1, fig.cap=ifelse(french, "(ref:wcvi-autocor-cap-fr)", "(ref:wcvi-autocor-cap)")}
make.autocor.plot(major_models[[model_ind]], mcmc_burnin = 1000)
```

(ref:wcvi-pairs-cap) West Coast of Vancouver Island SAR:
pairs plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables}, and Figure \@ref(fig:hg-traces) for description.

(ref:wcvi-pairs-cap-fr) Diagrammes par paires des résultats de simulation Monte Carlo par chaîne de Markov pour
les paramètres estimés pour le hareng du Pacifique dans la region d’évaluation des stocks majeur de la côte ouest de l’île de Vancouver.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}, et la figure \@ref(fig:hg-traces) pour la description.

```{r wcvi-pairs, fig.asp=1, fig.cap=ifelse(french, "(ref:wcvi-pairs-cap-fr)", "(ref:wcvi-pairs-cap)")}
make.pairs.plot(major_models[[model_ind]],
                params=c("ro", "h", "m", "rbar", "rinit", "q1", "q2", "sel1",
                         "selsd1", "sel2", "selsd2", "sel3", "selsd3"))
```

(ref:wcvi-biomass-retro-cap) West Coast of Vancouver Island SAR:
maximum posterior density of spawning biomass in thousands of tonnes (t; lines)
from `r new_surv_yr` to `r assess_yr` (base model) with retrospectives 
(-`r min(retrospective_yrs)` to -`r max(retrospective_yrs)` years)
for the Pacific Herring statistical catch-age model.
See Figure \@ref(fig:hg-biomass-retro) for description.

(ref:wcvi-biomass-retro-cap-fr) Densité a posteriori maximale de la biomasse reproductrice en milliers de tonnes (t; lignes)
de `r new_surv_yr` à `r assess_yr` (modèle de base) avec des rétrospectives
(-`r min(retrospective_yrs)` à -`r max(retrospective_yrs)` années)
pour le hareng du Pacifique dans la
région d'évaluation des stocks majeur de la côte ouest de l’île de Vancouver.
Voir la figure \@ref(fig:hg-biomass-retro) pour la description.

```{r wcvi-biomass-retro, fig.asp=0.65, fig.cap=ifelse(french, "(ref:wcvi-biomass-retro-cap-fr)", "(ref:wcvi-biomass-retro-cap)")}
biomass.plot.mpd(major_models[[model_ind]],
                 xlim = c(new_surv_yr, assess_yr),
                 df = major_surv %>% filter(region == major_regions_full[model_ind]),
                 translate = french)
```

(ref:wcvi-sr-cap) West Coast of Vancouver Island SAR:
relationship between spawning biomass in thousands of tonnes (t) and
the number of age-`r age_first` recruits in thousands of millions (points),
as well as the predicted Beverton-Holt stock-recruitment relationship (line)
for the Pacific Herring statistical catch-age model.
See Figure \@ref(fig:hg-sr) for description.

(ref:wcvi-sr-cap-fr) La relation entre la biomasse reproductrice en milliers de tonnes (t) et
le nombre de recrues d'âge `r age_first` en milliers de millions (points), ainsi que
la relation stock-recrutement du modèle Beverton-Holt prévue (ligne)
pour le hareng du Pacifique dans la région d’évaluation des stocks majeur de la côte ouest de l’île de Vancouver.
Voir la figure \@ref(fig:hg-sr) pour la description.

```{r wcvi-sr, fig.asp=0.4, fig.cap=ifelse(french, "(ref:wcvi-sr-cap-fr)", "(ref:wcvi-sr-cap)")}
plot_bh(major_models[[model_ind]],
        regions=major_regions_full[[model_ind]],
        translate=french)
```
