# West Coast of Vancouver Island diagnostics

This section contains Markov chain Monte Carlo (MCMC) diagnostics
for the Pacific Herring statistical catch-age model
in the West Coast of Vancouver Island major stock assessment region.
The MCMC run had chain length `r f(mcmc_length)`
with a sample taken every `r f(mcmc_samp_freq)`^th^ iteration (i.e., thinning).
The first `r f(mcmc_burnin)` samples were discarded (i.e., burn-in),
leaving `r f(mcmc_num_samples)` samples for posteriors.
This section will not be included in the final document.

Autocorrelation was detected in the estimation of
fishery selectivity-at-50% ($\hat{a}_1$) and
its standard deviation ($\hat{\gamma}_1$) for the "other" fisheries category
In 2021 we attempted to ameliorate the issue by
using posterior medians from 2020 as starting values,
increasing the MCMC chain from 5 million to 10 million iterations, and
increasing the number of initial iterations discarded as burn-in from
1,000 to 5,000, and then again to 7,000.
The thinning rate, choosing 1 out of every 1,000 was kept the same. 
The autocorrelation for both $\hat{a}_1$ and $\hat{\gamma}_1$ was reduced
but still persistent. 
An attempt to run the chain for 20 million iterations, with a 1 in 4,000 thin rate, was also made but was not successful due to computer limitations. 
Since these remedies did not eliminate the autocorrelation, and
had little impact on the estimation of $SB_t$ and $SB_0$ in 2021, 
we have reported the results of the 5 million-run chain
to be consistent with other SARs.

(ref:wcvi-priors-posts-cap) West Coast of Vancouver Island SAR:
prior probability distributions (lines) with
comparative posterior histograms (bars)
for the Pacific Herring statistical catch-age model.
See Table \@ref(tab:hg-parameter-est) and
Figure \@ref(fig:hg-priors-posts) for description.

(ref:wcvi-priors-posts-cap-fr) Distributions de probabilité a priori (lignes)
et histogrammes a posteriori comparatifs (barres)
pour le hareng du Pacifique dans
la région d’évaluation des stocks majeur de la côte ouest de l’île de Vancouver.
Voir le tableau \@ref(tab:hg-parameter-est) et
la figure \@ref(fig:hg-priors-posts) pour la description.

```{r wcvi-priors-posts, fig.cap=ifelse(french, "(ref:wcvi-priors-posts-cap-fr)", "(ref:wcvi-priors-posts-cap)")}
model_ind <- match(en2fr("WCVI", french), major_regions_short)
make.priors.posts.plot(
  model = major_models[[model_ind]],
  priors.only = FALSE
  )
```

(ref:wcvi-traces-cap) West Coast of Vancouver Island SAR:
trace plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables}, and
Figure \@ref(fig:hg-traces) for description.

(ref:wcvi-traces-cap-fr) Tracés des résultats de
simulation Monte Carlo par chaîne de Markov pour les paramètres estimés
pour le hareng du Pacifique dans
la région d’évaluation des stocks majeur de la côte ouest de l’île de Vancouver.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}, et
la figure \@ref(fig:hg-traces) pour la description.

```{r wcvi-traces, fig.asp=1, fig.cap=ifelse(french, "(ref:wcvi-traces-cap-fr)", "(ref:wcvi-traces-cap)")}
make.traces.plot(
  model = major_models[[model_ind]],  mcmc_burnin = mcmc_burnin
)
```

(ref:wcvi-autocor-cap) West Coast of Vancouver Island SAR:
autocorrelation plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables}, and
Figure \@ref(fig:hg-traces) for description.

(ref:wcvi-autocor-cap-fr) Diagrammes d’autocorrélation des résultats de
simulation Monte Carlo par chaîne de Markov pour les
paramètres estimés pour le hareng du Pacifique dans
la région d’évaluation des stocks majeur de la côte ouest de l’île de Vancouver.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}, et
la figure \@ref(fig:hg-traces) pour la description.

```{r wcvi-autocor, fig.asp=1, fig.cap=ifelse(french, "(ref:wcvi-autocor-cap-fr)", "(ref:wcvi-autocor-cap)")}
make.autocor.plot(
  model = major_models[[model_ind]], mcmc_burnin = mcmc_burnin
)
```

(ref:wcvi-pairs-cap) West Coast of Vancouver Island SAR:
pairs plots for Markov chain Monte Carlo output of
estimated parameters for the Pacific Herring statistical catch-age model.
See Tables \@ref(tab:hg-parameter-est) and \ref{tab:variables}, and
Figure \@ref(fig:hg-traces) for description.

(ref:wcvi-pairs-cap-fr) Diagrammes par paires des résultats de
simulation Monte Carlo par chaîne de Markov pour
les paramètres estimés pour le hareng du Pacifique dans
la region d’évaluation des stocks majeur de la côte ouest de l’île de Vancouver.
Voir les tableaux \@ref(tab:hg-parameter-est) et \ref{tab:variables}, et
la figure \@ref(fig:hg-traces) pour la description.

```{r wcvi-pairs, fig.asp=1, fig.cap=ifelse(french, "(ref:wcvi-pairs-cap-fr)", "(ref:wcvi-pairs-cap)")}
make.pairs.plot(
  model = major_models[[model_ind]],
  params = c(
    "ro", "h", "m", "rbar", "rinit", "q1", "q2", "sel1", "selsd1", "sel2",
    "selsd2", "sel3", "selsd3"
  )
)
```

(ref:wcvi-biomass-retro-cap) West Coast of Vancouver Island SAR:
maximum posterior density (MPD)
of spawning biomass in thousands of tonnes (t; lines)
from `r new_surv_yr` to `r assess_yr` (base model) with retrospectives 
(-`r min(retro_yrs)` to -`r max(retro_yrs)` years)
for the Pacific Herring statistical catch-age model.
See Figure \@ref(fig:hg-biomass-retro) for description.

(ref:wcvi-biomass-retro-cap-fr) Densité a posteriori maximale  (DPM)
de la biomasse reproductrice en milliers de tonnes (t; lignes)
de `r new_surv_yr` à `r assess_yr` (modèle de base) avec des rétrospectives
(-`r min(retro_yrs)` à -`r max(retro_yrs)` années)
pour le hareng du Pacifique dans la
région d'évaluation des stocks majeur de la côte ouest de l’île de Vancouver.
Voir la figure \@ref(fig:hg-biomass-retro) pour la description.

```{r wcvi-biomass-retro, fig.asp=0.65, fig.cap=ifelse(french, "(ref:wcvi-biomass-retro-cap-fr)", "(ref:wcvi-biomass-retro-cap)")}
biomass.plot.mpd(
  model = major_models[[model_ind]],
  xlim = c(new_surv_yr, assess_yr),
  df = major_surv %>% filter(region == major_regions_full[model_ind]),
  translate = french
)
```

(ref:wcvi-sr-cap) West Coast of Vancouver Island SAR:
relationship between spawning biomass in thousands of tonnes (t) and
the number of age-`r age_first` recruits in thousands of millions (points),
as well as the predicted Beverton-Holt stock-recruitment relationship (line)
for the Pacific Herring statistical catch-age model.
See Figure \@ref(fig:hg-sr) for description.

(ref:wcvi-sr-cap-fr) La relation entre la biomasse reproductrice
en milliers de tonnes (t) et
le nombre de recrues d'âge `r age_first` en milliers de millions (points),
ainsi que la relation stock-recrutement du modèle Beverton-Holt prévue (ligne)
pour le hareng du Pacifique dans
la région d’évaluation des stocks majeur de la côte ouest de l’île de Vancouver.
Voir la figure \@ref(fig:hg-sr) pour la description.

```{r wcvi-sr, fig.asp=0.4, fig.cap=ifelse(french, "(ref:wcvi-sr-cap-fr)", "(ref:wcvi-sr-cap)")}
plot_bh(
  model = major_models[[model_ind]],
  regions = major_regions_full[[model_ind]],
  translate = french
)
```

(ref:hcr-wcvi-1-cap) West Coast of Vancouver Island SAR:
projected spawning biomass for `r assess_yr + 1` $\SB_{`r assess_yr+1`}$
compared to harvest rate (HR) and total allowable catch (TAC;
rows 2 to 7 in Table \@ref(tab:decision-wcvi)).
See Figure \@ref(fig:hcr-prd-1) for description.

```{r hcr-wcvi-1, fig.asp=1, fig.cap="(ref:hcr-wcvi-1-cap)"}
region <- "WCVI"
probs <- confidence_vals
cowplot::plot_grid(
  plot_hcr(
    hcr.lst = mp.lst.wcvi[[1]][[2]],
    sbt.lst = sbt.wcvi,
    mp = mp.wcvi[2, ]$label,
    region = region,
    probs = probs
  ),
  plot_hcr(
    hcr.lst = mp.lst.wcvi[[1]][[3]],
    sbt.lst = sbt.wcvi,
    mp = mp.wcvi[3, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  plot_hcr(
    hcr.lst = mp.lst.wcvi[[1]][[4]],
    sbt.lst = sbt.wcvi,
    mp = mp.wcvi[4, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  plot_hcr(
    hcr.lst = mp.lst.wcvi[[1]][[5]],
    sbt.lst = sbt.wcvi,
    mp = mp.wcvi[5, ]$label,
    region = region,
    probs = probs
  ),
  plot_hcr(
    hcr.lst = mp.lst.wcvi[[1]][[6]],
    sbt.lst = sbt.wcvi,
    mp = mp.wcvi[6, ]$label,
    region = region,
    probs = probs
  ),
  plot_hcr(
    hcr.lst = mp.lst.wcvi[[1]][[7]],
    sbt.lst = sbt.wcvi,
    mp = mp.wcvi[7, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  nrow = 3,
  ncol = 2,
  align = "hv",
  axis = "tblr"
)
```

(ref:hcr-wcvi-2-cap) West Coast of Vancouver Island  SAR:
projected spawning biomass for `r assess_yr + 1` $\SB_{`r assess_yr+1`}$
compared to harvest rate (HR) and total allowable catch (TAC;
rows 9 to 14 in Table \@ref(tab:decision-wcvi)).
See Figure \@ref(fig:hcr-prd-1) for description.

```{r hcr-wcvi-2, fig.asp=1, fig.cap="(ref:hcr-wcvi-2-cap)"}
region <- "SoG"
probs <- confidence_vals
cowplot::plot_grid(
  plot_hcr(
    hcr.lst = mp.lst.wcvi[[1]][[9]],
    sbt.lst = sbt.wcvi,
    mp = mp.wcvi[9, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  plot_hcr(
    hcr.lst = mp.lst.wcvi[[1]][[10]],
    sbt.lst = sbt.wcvi,
    mp = mp.wcvi[10, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  plot_hcr(
    hcr.lst = mp.lst.wcvi[[1]][[11]],
    sbt.lst = sbt.wcvi,
    mp = mp.wcvi[11, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  plot_hcr(
    hcr.lst = mp.lst.wcvi[[1]][[12]],
    sbt.lst = sbt.wcvi,
    mp = mp.wcvi[12, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  plot_hcr(
    hcr.lst = mp.lst.wcvi[[1]][[13]],
    sbt.lst = sbt.wcvi,
    mp = mp.wcvi[13, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  plot_hcr(
    hcr.lst = mp.lst.wcvi[[1]][[14]],
    sbt.lst = sbt.wcvi,
    mp = mp.wcvi[14, ]$label,
    region = region,
    probs = probs,
    show.x.axes = TRUE
  ),
  nrow = 3,
  ncol = 2,
  align = c("v", "h")
)
```
